---
title:  |
        | The Effect of Legislature Size on Public Spending
        | A Meta-Analysis
author: 
  - Huzeyfe Alptekin[^huzeyfe]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
  - Catarina Roman[^catarina]
date: \today
thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at <https://github.com/danilofreire/distributive-politics-meta-analysis>. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending. Based on a sample of 29 articles, we find no robust evidence for the effect of legislature size on government budgets. Yet the aggregate results show significant heterogeneity. While earlier studies provide moderate support for the \"law of $1/n$\", papers using modern causal inference methods consistently find a negative relationship between seats and spending. The available evidence also indicates that proportional representation and mixed voting systems are no more likely to overspend than majoritarian ones."
abstractspacing: double
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Clean up
rm(list = ls())

## Starting
set.seed(732578) # From random.org

# Needed packages
pkgs <- c("tidyverse", "meta", "metafor",
          "readxl", "data.table",
          "knitr", "gridGraphics", "gridExtra",
          "ggpubr", "kableExtra", "magick")

# Install if not already installed
installIfNot <- function(x) {
  if (x %in% rownames(installed.packages()) == FALSE)
    install.packages(x, dependencies = T,
					 repos = "http://cran.us.r-project.org")
}
lapply(pkgs, installIfNot)

# Load packages
lapply(pkgs, require, character.only = T)
devtools::install_github("isubirana/compareGroups")
library("compareGroups")

# Load datasets
load("../dataset/dataCoefs.RData")

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(mod$lower.random,
                          mod$lower.predict),
                upper = c(mod$upper.random,
                          mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()

  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

# Build forest plot for heterogeneous analysis
# Build plot function for forest plots
build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod <- update(mod, byvar = hetvar, print.byvar = F)
  
  # Build dataset for plot
  mod2 <- tibble(
    byvar = mod$byvar,
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    arrange(byvar)
  auxmod <- tibble()
  for (i in rev(mod$bylevs)){
    auxmod <- rbind(auxmod, tibble(byvar = i,
                    TE = NA,
                    seTE = NA,
                    studlab = toupper(i),
                    lower = NA,
                    upper = NA,
                    group = "B"))
    auxmod <- rbind(auxmod, 
                    filter(mod2, byvar==i) %>% 
                      arrange(desc(TE)))
    auxmod <- rbind(auxmod, tibble(
      byvar = i,
      TE = mod$TE.random.w[which(mod$bylevs==i)],
      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
      studlab = 'Subgroup Effect',
      lower = mod$lower.random.w[which(mod$bylevs==i)],
      upper = mod$upper.random.w[which(mod$bylevs==i)],
      group = "B"))
  }
  auxmod <- rbind(auxmod, tibble(
    byvar = NA,
    TE = c(mod$TE.random, NA),
    seTE = c(mod$seTE.random, NA),
    studlab = c("Overall Effect", "Prediction Interval"),
    lower = c(mod$lower.random, mod$lower.predict),
    upper = c(mod$upper.random, mod$upper.predict),
    group = "B"))
  mod2 <- data.frame(auxmod)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
  
  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))
  
  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}
```

[^huzeyfe]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.

[^danilo]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.

[^catarina]: Research Associate, School of International Relations, Fundação Getulio Vargas, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

\newpage

# Introduction
\label{sec:intro}

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Most
early studies that empirically tested the "law of $1/n$", as the theory is
currently known, indeed found a positive correlation between the number of
legislature seats and different measures of government spending, although the
effect was often limited to one house [e.g., @baqir2002districting;
@gilligan1995deviations; @gilligan2001fiscal]. Recent research has further
questioned the validity of the "law of $1/n$". For instance, spending limits,
bicameralism, or strong executives may reduce the inefficiency of pork barrel
projects [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop].
Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending. 

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Given this diversity of empirical
findings, a systematic review of the existing evidence may help us reach a
meaningful conclusion about the effect of legislature size on public spending.
Meta-analysis is the most appropriate method for this task. Meta-analysis
combines the outcomes of multiple studies into a single estimation and allows
scholars to draw robust conclusions from the aggregated data
[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy].

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that
use quantitative methods to assess the impact of legislature size over
government spending across several dimensions. We run two sets of models: the
first group uses only the main estimates of each selected paper (`r dim(dat)[1]`),
while the second set includes all coefficients reported in our
sample (`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))`
papers in our review, we include `r dim(dat)[1]` coefficients in the restricted 
sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles 
report separate estimates for the impact of lower and upper house size on 
government expenditures. In the full model, we add every outcome reported in the 
papers, regardless of whether the coefficient comes from the main tables or from 
robustness checks. We discuss our sampling process in the Methods section and in 
the Supplementary Material.}
Our independent variables consist of three measures, namely the size of the
lower chamber ($n$), its natural logarithm (log($n$)), and the number of members
in the upper chamber ($k$). We evaluate their effect upon public expenditure per
capita, the natural logarithm of public expenditure per capita, and government
expenditure as a percentage of GDP. We then estimate if the results vary
according to four potential sources of effect heterogeneity.

Aggregate results show that legislative size has no significant impact on public
spending. However, the meta-regressions suggest that our study sample has high
levels of heterogeneity, and effects differ substantially according to study
specifications. A reliable predictor of effect size is the research method
employed in the original paper. While papers that employ conventional linear
regressions often find a positive relation between legislature size and
government budgets, recent studies using new methods of causal inference,
specially those with regression discontinuity designs, provide consistent
evidence for a negative relation. This goes in contrast with the original theory
and supports the existence of a "reverse law of $1/n$". Additionally, we find
that non-majoritarian voting systems decrease government spending as a
percentage of GDP, which is also evidence against the theoretical expectations
of the "law of $1/n$". In summary, we do not find support for the theory as
originally conceived, and causal inference models suggest that larger
legislatures are associated with lower public spending.

# Methods

We collected the study sample using three criteria. First, the study should cite
\citet{weingast1981political} as their work is foundational to the distributive
politics literature. Second, the study had to use quantitative methods to
estimate the relationship between our variables of interest.\footnote{As
meta-analysis requires a single estimate per observation, we excluded articles
that use interaction terms or quadratic specifications of our independent
variables.} Third, the study should be written in the English language. We
conducted a primary search using Scopus, Microsoft Academic, and Google Scholar,
three large academic databases.\footnote{See the Supplementary Material for code.}

After applying our exclusion criteria, the search produced a dataset of `r length(unique(dat$id))` 
studies as of the 21\textsuperscript{st} of November, 2019. Table
\ref{tab:papers} contains the full list of articles from which we drew data. A
PRISMA\footnote{The Preferred Reporting Items for Systematic Reviews and
  Meta-Analyses (PRISMA) statement provides a checklist designed to improve the
quality and transparency of study selection processes in meta-analyses. For more
information on the PRISMA framework, see \citet{liberati2009prisma}.} flow
diagram showing the number of resulting papers after each review step is
available in the Supplementary Material.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.4cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
\tabularnewline
\midrule
\endhead
```{r, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authorCite, title, journalCode, year, locationISO, method, elecsys3) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authorCite[i]), ' & ', aux$title[i], ' & ',
      aux$journalCode[i], ' & ', aux$year[i], ' & ', 
      aux$locationISO[i], ' & ', aux$method[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal,
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation). Country codes
follow the ISO 3166-1 alpha-3 international standard.} \end{minipage}
\end{longtable}

\normalsize

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Five articles use cross-national data and analyse from 2 to 110
countries. Early studies employed OLS and panel data methods to analyse the
results, whereas the use of regression discontinuity designs is a recent
addition to the literature, starting in 2012.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
suggested by \citet{weingast1981political} and tested the impact of larger
legislatures on different measures of government spending. Our independent
variables of interest are $n$, lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), ($\log(n)$), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and $k$, which represents upper chamber
size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded four moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study ($n$,
log($n$), or $k$). The additional moderators are: 1) publication year; 2) paper
publication in an academic journal; 3) electoral system; 4) estimation method.
Since the literature on the "law of $1/n$" is notably diverse, we were
restricted to include only the moderators that either refer to important
theoretical questions, such as the effect of the electoral system on public
spending, or to essential characteristics of the publications themselves.
Although more moderators exist in the literature (ie., data aggregation level),
they do not appear as often as required for the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables. 

\vspace{.5cm}

```{r, echo = FALSE, results='hide', warning=FALSE, message=FALSE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
fulldat$usemeta2 <- as.character(fulldat$usemeta2)
fulldat$usemeta2 <- factor(fulldat$usemeta2)
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

res <- export2latex(
  descrTable(~.-usemeta2, aux, y = aux$usemeta2,
             show.p.overall = F, show.all = T, all.last = T), 
  caption = 'Descriptive statistics of moderators\\label{tab:descriptive}'
)
res <- gsub(pattern = '\\[ALL\\]', 'All Coefficients', res$desc, useBytes = T)
cat(res)
```

\footnotesize
\begin{longtable}{lccc}\caption{Descriptive Statistics of Moderators\label{tab:descriptive}}\\
\hline  
& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
&       N=42        &       N=100        &    N=142    \\
\hline
\hline     
\endfirsthead 
\multicolumn{4}{l}{\tablename\ \thetable{} \textit{-- continued from previous page}}\\ 
\hline
& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
&       N=42        &       N=100        &    N=142    \\ 
\hline
\hline  
\endhead   
\hline
\multicolumn{4}{l}{\textit{continued on next page}} \\ 
\endfoot   
\multicolumn{4}{l}{}  \\ 
\endlastfoot 
Independent Variables: &                   &                    &            \\ 
$\qquad$K &    12 (28.6\%)     &     33 (33.0\%)     & 45 (31.7\%) \\ 
$\qquad$N &    24 (57.1\%)     &     55 (55.0\%)     & 79 (55.6\%) \\ 
$\qquad$logN &     6 (14.3\%)     &     12 (12.0\%)     & 18 (12.7\%) \\ 
Year &    2009 (6.56)    &    2008 (5.82)     & 2008 (6.04)\\ 
Published work: &                   &                    &            \\ 
$\qquad$Yes &    36 (85.7\%)     &     93 (93.0\%)     & 129 (90.8\%)\\ 
$\qquad$No &     6 (14.3\%)     &     7 (7.00\%)      & 13 (9.15\%) \\ 
Electoral system: &                   &                    &            \\ 
$\qquad$Majoritarian &    22 (52.4\%)     &     46 (46.0\%)     & 68 (47.9\%) \\ 
$\qquad$Non-Majoritarian &    20 (47.6\%)     &     54 (54.0\%)     & 74 (52.1\%) \\ 
Estimation method: &                   &                    &            \\ 
$\qquad$OLS &    11 (26.2\%)     &     36 (36.0\%)     & 47 (33.1\%) \\ 
$\qquad$PANEL &    23 (54.8\%)     &     51 (51.0\%)     & 74 (52.1\%) \\ 
$\qquad$IV &     5 (11.9\%)     &     7 (7.00\%)      & 12 (8.45\%) \\ 
$\qquad$RDD &     3 (7.14\%)     &     6 (6.00\%)      &  9 (6.34\%)  \\ 
 
\hline
\end{longtable}

\normalsize

Since most selected articles have more than one effect size, the observations
in our dataset are not independent. To reduce the impact of multicollinearity,
we estimate the models using two sets of study coefficients. The first group
includes only the most rigorous model from each paper, that is, those estimated
with the largest $n$, most control variables, and fixed effects if the authors
added them. If the article employed a regression discontinuity design, we chose
the coefficient from the optimal bandwidth or from the intermediate one. This
sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
independent variables of interest \citep{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen_malhotra_2007, crowley2019law,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading}. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect
sizes reported in the `r length(unique(dat$id))` papers. Here we focus on the results for our restricted
sample as we consider them more robust, but the findings are very similar when
we use the extended set. We discuss eventual differences in the next section.
Please refer to the Supplementary Material for further information about our
sampling process and for the complete results.

# Results

## Binomial Z-Tests
\label{sub:binomial}

The "law of $1/n$" states that more legislators increase government expenditure.
Here we employ three methods to assess the empirical validity of that
relationship. First, we run a binomial one-proportion z-test to determine
whether the study coefficients have a positive or negative sign. Then, we fit 7
random-effect models using the \texttt{meta} \citep{balduzzi2019perform} and the
\texttt{dmetar} \citep{dmetar2019} packages for the \texttt{R} statistical
language \citep{rstats2019}. We estimate the true effect size variance
($\tau^2$) with a Restricted Maximum Likelihood Estimator, which the literature
considers the most precise for continuous dependent variables
\citep{veroniki2016methods}. Lastly, we run a series of meta-regressions to test
possible sources of result heterogeneity. To recapitulate, our independent
variables of interest are lower chamber size ($n$), the natural logarithm of
lower chamber size (log($n$)), and upper chamber size ($k$). The dependent
variables are public expenditure per capita, the natural logarithm of public
expenditure per capita, and government expenditure as a percentage of GDP. Since
the outcomes have different scales, we treat them separately in our models.

```{r, cache=TRUE, echo = FALSE}
aux <- filter(dat, indepvar2 == "N")
binN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux <- filter(dat, indepvar2=='K')
binK <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux <- filter(dat, indepvar2 == "logN")
binlogN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
```

The binomial z-test evaluates whether the coefficient of our independent
variables are positive or negative. The null hypothesis here states that the
sign of the coefficient is equally likely to be positive or negative. We start
with $n$, lower house size. Our results indicate that there is no correlation
between the number of legislators in the lower house and public expenditure 
(successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
association between both. The binomial test for log($n$) also shows a
non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
positive result for the number of legislators in the upper house ($k$), which is
in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binK$p.value), 3)`). 

## Meta-Analysis
\label{sub:Meta-Analysis}

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the 9 possible variable combinations, we found only 7 in
the article pool. Our sample includes no papers that analyse the relationships
between log($n$), and public expenditure per capita and between $k$ and the
logarithm of public expenditure per capita.

Figure \ref{fig:plots} shows the forest plots for our restricted sample, the one
which includes only the main `r dim(dat)[1]` coefficients for the 
`r length(unique(dat$id))` selected papers. On the left side of the plots are 
the name of the study authors and the paper publication year. For unpublished
studies, we included the first year the paper was available online. The bars in
the middle show the reported effect sizes and the vertical lines indicate their
average, weighted by standard errors. The length of the lines represent the
precision of the estimates. The red line at the bottom of the figures displays
the aggregate coefficients plus their respective confidence intervals.

```{r, echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE}
mod <- list()
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod[[1]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod[[2]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod[[3]] <- metagen(
  coef, SE, data=aux,
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction = TRUE,
  sm="SMD"
  )

# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

mod[[4]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod[[5]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

mod[[6]] <- metagen(
  coef, SE, data=aux,
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction=TRUE,
  sm="SMD"
  )

# Pooling effects analysis -- PCTGDP x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

mod[[7]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Full model - Pooling effects analysis -- PCTGDP x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod[[8]] <- metagen(coef, SE, data = aux,
          studlab = paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm = "SMD")

# Full data - Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod[[9]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
```

The first column of the graph reports the results for $n$, lower chamber size.
In the first model, which correlates $n$ and expenditure per capita, we find a
standardised mean difference (SMD) of `r round(mod[[1]]$TE.random,3)` and a standard error of `r round(mod[[1]]$seTE.random,3)`
(studies = `r mod[[1]]$k`, 95\% CI = [`r round(mod[[1]]$lower.random,3)`; `r round(mod[[1]]$upper.random,3)`], $p$-value = `r round(mod[[1]]$pval.random,3)` , prediction interval
= [`r round(mod[[1]]$lower.predict,3)`; `r round(mod[[1]]$upper.predict,3)`]). Therefore, we cannot reject the null hypothesis that the
effect size is zero. The $I^2$ statistic, which quantifies the degree of
heterogeneity among studies, is equal to `r round(mod[[1]]$I2*100, 2)`\%. $I^2$ values above 75\%
indicate very high study heterogeneity [@higgins2019cochrane].

We see similar results when we compare $n$ with log expenditure per capita. In
this model, the average effect size is `r round(mod[[3]]$TE.random,3)` and the standard error is
`r round(mod[[3]]$seTE.random,3)` (studies = `r mod[[3]]$k`, 95\% CI = [`r round(mod[[3]]$lower.random,3)`; `r round(mod[[3]]$upper.random,3)`], $p$-value = `r round(mod[[3]]$pval.random,3)`, prediction
interval = [`r round(mod[[3]]$lower.predict,3)`; `r round(mod[[3]]$upper.predict,3)`]; $I^2$ = `r round(mod[[3]]$I2*100, 2)`\%). The coefficient is 
statistically indistinguishable from zero.

In our restricted sample, larger lower house size also does not increase
government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD = `r round(mod[[5]]$TE.random,3)`, SE =
`r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
[`r round(mod[[5]]$lower.predict,3)`; `r round(mod[[5]]$upper.predict,3)`], $I^2$ = `r round(mod[[5]]$I2*100, 2)`\%). We find a positive effect in our extended
sample and the coefficient is statistically significant at the 10\% level
(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; `r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
result supports the "law of 1/$n$", but the evidence is moderate
as the prediction interval include zero.

\begin{landscape}
\begin{figure}[p]
\begin{center}
\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
\vspace{.3cm}
\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
\label{fig:plots}
\end{center}
\end{figure}
\end{landscape}

Next, we present the meta-analyses using log($n$), the logarithm of lower house
size, as the main explanatory variable. We start with the relationship between
log($n$) and the logarithm of expenditure per capita. The result is positive and
statistically significant at 10\%, but the prediction interval encompasses zero
(studies = `r mod[[4]]$k`, SMD = `r round(mod[[4]]$TE.random,3)`, SE = `r round(mod[[4]]$seTE.random,3)`, 95\% CI = [`r round(mod[[4]]$lower.random,3)`; `r round(mod[[4]]$upper.random,3)`], $p$-value =
`r round(mod[[4]]$pval.random,3)`, prediction interval = [`r round(mod[[4]]$lower.predict,3)`; `r round(mod[[4]]$upper.predict,3)`], $I^2$ = `r round(mod[[4]]$I2*100, 2)`\%). Although the
coefficient has the predicted sign, we should interpret the finding with caution
as it does not replicate in our sample of `r dim(fulldat)[1]` effect sizes.

Our model that correlates log($n$) with public expenditures as a percentage of
GDP fails to reach conventional levels of statistical significance (studies =
`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = `r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`; `r round(mod[[6]]$upper.random,3)`], $p$-value = `r round(mod[[6]]$pval.random,3)`,
prediction interval = [`r round(mod[[6]]$lower.predict,3)`; `r round(mod[[6]]$upper.predict,3)`], $I^2$ = `r round(mod[[6]]$I2*100, 2)`\%). The extended sample
also gives us a null result.

The third set of models uses $k$, upper house size, as the main independent
variable. We find a positive correlation between $k$ and expenditure per capita
but the coefficient is not significant (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
= `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
[`r round(mod[[2]]$lower.predict,3)`; `r round(mod[[2]]$upper.predict,3)`], $I^2$ = `r round(mod[[2]]$I2*100, 2)`\%). But as with the other models, the prediction
interval again includes zero. When we run the same analysis in the extended
sample, we see a significant coefficient for the estimate, yet the prediction interval also
contains zero (coefficients = `r mod[[9]]$k`, SMD = `r round(mod[[9]]$TE.random,3)`, SE = `r round(mod[[9]]$seTE.random,3)`, 95\% CI = [`r round(mod[[9]]$lower.random,3)`; `r round(mod[[9]]$upper.random,3)`],
$p$-value $<$ 0.001, prediction interval = [`r round(mod[[9]]$lower.predict,3)`; `r round(mod[[9]]$upper.predict,3)`], $I^2$ = `r round(mod[[9]]$I2*100, 2)`\%).

Our last estimation analyses the relationship between $k$ and government
spending as a percentage of GDP. The coefficient is not statistically
significant, indicating a null effect (studies = `r mod[[7]]$k`, SMD = `r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI
= [`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`], $p$-value = `r round(mod[[7]]$pval.random,3)`, prediction interval = [`r round(mod[[7]]$lower.predict,3)`; `r round(mod[[7]]$upper.predict,3)`],
$I^2$ = `r round(mod[[7]]$I2*100, 2)`\%). The result is very similar in the extended sample.

In a nutshell, we find no robust evidence in favour of the "law of $1/n$".
While some models do show a positive and statistically significant result, none
of the prediction intervals are totally positive or negative. The studies also
have considerable heterogeneity, what indicates that the original coefficients
do not point consistently towards the same direction.

One reason why we have not detected any strong effects may be due to the
identification strategy authors use in their models. On the one hand, OLS and
panel data models require too many controls to make units comparable, and they
are also vulnerable to omitted variable bias or post-treatment bias
[@cinelli2020making; @pearl2015conditioning]. On the other hand, estimation
methods such as instrumental variables and, in particular, regression
discontinuity designs have become popular because of their internal validity
[@angrist2008mostly]. Figure \ref{fig:plots2} shows the disaggregated effects for
two sets of models that employ causal estimation techniques. They measure the
impact of lower house size on expenditure per capita (left) and on the natural
logarithm of expenditure per capita (right).

\newpage 

\begin{figure}[htb!]
\begin{center}
\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (restricted sample)}
\vspace{.3cm}
\includegraphics[width=1\linewidth]{../graphs/graph2.pdf}
\label{fig:plots2}
\end{center}
\end{figure}

Papers that employed instrumental variables show an interesting variation: out
of the four coefficients listed, two are positive and two are negative. Two of
these four coefficients are significant, again one positive and one negative.
The subgroup analysis presents a SMD which is negative but insignificant. In
contrast, all papers that use regression discontinuity designs show negative and
statistically significant results. Since only three papers in our sample use
RDDs, we are cautious about predicting an overall negative relation, but they do
indicate that better identification strategies yield a zero-to-negative impact
of legislature size on expenditure, in support of the reverse "law of $1/n$".

## Meta-Regressions
\label{sub:regressions}

In this section, we run a series of meta-regressions with covariates that may
account for differences across the selected papers. The first variable indicates
whether the study uses $n$, log($n$) or $k$ as its main explanatory variable.
The second variable shows the study publication year, which we included to
capture temporal variation in the study coefficients. We also add a dummy
variable to assess whether published articles report effect sizes that are
higher or lower than those from working papers. The fourth variable measures
whether studies focusing on non-majoritarian electoral systems report
coefficients that are smaller or larger than those from majoritarian countries.
Our last covariate is a categorical variable indicating the statistical
procedure used in the original models (panel data, instrumental variables,
OLS, or regression discontinuity design).

Table \ref{tabregressions} presents the meta-regression results for our
restricted and extended samples. Each column represents one of the three
measures of public spending we discuss in this paper. To reduce the risk of
false positives in our analyses, we use permutation tests to calculate
significance levels for the meta-regressions \citep{higgins2004controlling}.

```{r, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = TRUE}
res <- list()

## Expenditure as percentage GDP -- Restricted
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)

res[[1]] <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Elecsys: Non-Majoritarian",
             "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

## Expenditure as percentage GDP -- Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)

res[[2]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Indepvar: logN",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Expenditure per capita - Restricted
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear,
            control=list(maxiter=1000))

res[[3]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Expenditure per capita - Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)

res[[4]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Log of Expenditure per capita - Restricted
mod <- rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)

res[[5]] <- tibble(
   ` ` = c("Intercept",
           "Indepvar: N",
           "Year",
           "Published: No",
           "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Log of Expenditure per capita - Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)

res[[6]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel",
          "Method: RDD"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
strep <- function (x) {
  ifelse(x<0.01, '***',ifelse(x<0.05,'**', ifelse(x<0.1,'*','')))
}
```

```{=latex}
\vspace{0.5cm}

\begin{table}[htpb]
\caption{Meta Regression Results\label{tabregressions}}
\footnotesize
\centering
\begin{tabular}{lcccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Independent Variable: $N$ & `r round(res[[3]][2,2],3)` & `r round(res[[4]][2,2],3)` & `r round(res[[5]][2,2],3)` & `r round(res[[6]][2,2],3)` & `r round(res[[1]][2,2],3)` & `r round(res[[2]][2,2],3)`\\
                          & (`r round(res[[3]][2,3],3)`)`r strep(res[[3]][2,5])` & (`r round(res[[4]][2,3],3)`)`r strep(res[[4]][2,5])` & (`r round(res[[5]][2,3],3)`)`r strep(res[[5]][2,5])` & (`r round(res[[6]][2,3],3)`)`r strep(res[[6]][2,5])` & (`r round(res[[1]][2,3],3)`)`r strep(res[[1]][2,5])` & (`r round(res[[2]][2,3],3)`)`r strep(res[[2]][2,5])`\\
%
Independent Variable: log($N$) &  &  &  &  & `r round(res[[1]][3,2],3)` & `r round(res[[2]][3,2],3)`\\
                               &  &  &  &  & (`r round(res[[1]][3,3],3)`)`r strep(res[[1]][3,5])` & (`r round(res[[2]][3,3],3)`)`r strep(res[[2]][3,5])`\\
%
Year & `r round(res[[3]][3,2],3)` & `r round(res[[4]][3,2],3)` & `r round(res[[5]][3,2],3)` & `r round(res[[6]][3,2],3)` & `r round(res[[1]][4,2],3)` & `r round(res[[2]][4,2],3)`\\
     & (`r round(res[[3]][3,3],3)`)`r strep(res[[3]][3,5])` & (`r round(res[[4]][3,3],3)`)`r strep(res[[4]][3,5])` & (`r round(res[[5]][3,3],3)`)`r strep(res[[5]][3,5])` & (`r round(res[[6]][3,3],3)`)`r strep(res[[6]][3,5])` & (`r round(res[[1]][4,3],3)`)`r strep(res[[1]][4,5])` & (`r round(res[[2]][4,3],3)`)`r strep(res[[2]][4,5])`\\
%
Published: No & `r round(res[[3]][4,2],3)` & `r round(res[[4]][4,2],3)` & `r round(res[[5]][4,2],3)` &  `r round(res[[6]][4,2],3)` &  & \\
              & (`r round(res[[3]][4,3],3)`)`r strep(res[[3]][4,5])` & (`r round(res[[4]][4,3],3)`)`r strep(res[[4]][4,5])` & (`r round(res[[5]][4,3],3)`)`r strep(res[[5]][4,5])` & (`r round(res[[6]][4,3],3)`)`r strep(res[[6]][4,5])` &  & \\
%
Non-Majoritarian (PR \& Mixed) & `r round(res[[3]][5,2],3)` & `r round(res[[4]][5,2],3)` & &  & `r round(res[[1]][5,2],3)` & `r round(res[[2]][5,2],3)` \\
                               & (`r round(res[[3]][5,3],3)`)`r strep(res[[3]][5,5])` & (`r round(res[[4]][5,3],3)`)`r strep(res[[4]][5,5])` & &  & (`r round(res[[1]][5,3],3)`)`r strep(res[[1]][5,5])` & (`r round(res[[2]][5,3],3)`)`r strep(res[[2]][5,5])`\\
%
Method: Panel & `r round(res[[3]][6,2],3)` & `r round(res[[4]][6,2],3)` & `r round(res[[5]][5,2],3)` & `r round(res[[6]][5,2],3)` & `r round(res[[1]][6,2],3)` & `r round(res[[2]][6,2],3)`\\
              & (`r round(res[[3]][6,3],3)`)`r strep(res[[3]][6,5])` & (`r round(res[[4]][6,3],3)`)`r strep(res[[4]][6,5])` & (`r round(res[[5]][5,3],3)`)`r strep(res[[5]][5,5])` & (`r round(res[[6]][5,3],3)`)`r strep(res[[6]][5,5])` & (`r round(res[[1]][6,3],3)`)`r strep(res[[1]][6,5])` & (`r round(res[[2]][6,3],3)`)`r strep(res[[2]][6,5])`\\
%
Method: IV & `r round(res[[3]][7,2],3)` & `r round(res[[4]][7,2],3)` &  &  &  & \\
           & (`r round(res[[3]][7,3],3)`)`r strep(res[[3]][7,5])` & (`r round(res[[4]][7,3],3)`)`r strep(res[[4]][7,5])` &  &  &  & \\
%
Method: RDD &  &  &  & `r round(res[[6]][6,2],3)` &  & \\
            &  &  &  & (`r round(res[[6]][6,3],3)`)`r strep(res[[6]][6,5])` &  & \\
% 
Intercept & `r round(res[[3]][1,2],3)` & `r round(res[[4]][1,2],3)` & `r round(res[[5]][1,2], 3)` & `r round(res[[6]][1,2], 3)` & `r round(res[[1]][1,2], 3)` & `r round(res[[2]][1,2], 3)`\\
          & (`r round(res[[3]][1,3],3)`)`r strep(res[[3]][1,5])` & (`r res[[4]][1,3]`)`r strep(res[[4]][1,5])` & (`r round(res[[5]][1,3],3)`)`r strep(res[[5]][1,5])` & (`r round(res[[6]][1,3],3)`)`r strep(res[[6]][1,5])` & (`r round(res[[1]][1,3],3)`)`r strep(res[[1]][1,5])` & (`r round(res[[2]][1,3],3)`)`r strep(res[[2]][1,5])`\\
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include `r length(dat$id)` and `r length(fulldat$id)` study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$. Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.}}
\end{minipage}
\end{table}
```

The first two models show the results for public expenditure per capita. No
variable reaches conventional levels of statistical significance in the
restricted sample. In the extended sample, we find that models that use $n$ as
an independent variable have lower effects when
compared to $k$. This suggests that an additional member in the lower house has
a smaller impact on public spending than a member in the upper house. Moreover,
the results for the extended sample point out that recent studies find larger
effects than older ones.

The third and fourth columns use the natural logarithm of expenditure per capita
as the dependent variable. None of the covariates are statistically significant in our
smaller sample, but two moderators are negatively associated with the outcome in
our larger study pool. They both refer to estimation methods. Studies that
employ panel/fixed effects or regression discontinuity designs (RDDs) have lower
coefficients for log expenditure per capita if we take OLS as the reference
category. 

Two variables are statistically significant in the last set of meta-regressions,
which include public expenditures as a percentage of GDP as the dependent
variable. Both in our restricted and in our extended samples, recent studies
have smaller coefficients than early papers, which stands in contrast with
our previous models. Non-majoritarian voting systems are also
associated with lower levels of public spending, what is against the theoretical
expectations of the "law of $1/n$". The results, however, do not replicate in
the first set of estimations.

Overall, our results suggest that study coefficients are highly sensitive to
research design choices. The same study samples may produce different outcomes
depending on the response variables scholars decide to analyse. Moreover, we
find evidence that results vary considerably if the study employs different
measures of legislature size or use causal research methods. The impact of
factors such as the electoral system or year of publication also appear to be
conditional on the selected model.

# Discussion
\label{sec:discussion}

In this article, we assess the empirical validity of the "law of $1/n$". Based
on a sample of `r length(unique(dat$id))` publications on the topic, our
meta-analyses show that there is no strong evidence that an increase in the
number of legislators has a significant effect on public expenditures. If such
effect exists, it is likely driven by an increase in $k$, the size of the upper
legislature, as suggested by several studies in the literature
[@baqir2002districting; @bradbury2001legislative; @bradbury2003local;
@chen_malhotra_2007; @gilligan2001fiscal; @primo2006stop]. Instead, we find
better evidence for the "reverse law of $1/n$", which posits that larger
legislatures lead to lower government spending. This is mainly because studies
using regression discontinuity designs, a method that has robust internal
validity, consistently indicate a negative relationship between lower house size
and the logarithm of expenditure per capita [@hohmann2017effect;
@lewis2019legislature; @petterssonlidbom2012size].

The meta-regressions indicate that study characteristics have a considerable
influence on reported results. Factors such as the electoral system affects the
relationship between legislature size and public expenditure, but the results
are not replicable in all estimations. Publication year also produces
conflicting findings in our models. Nevertheless, the meta-regressions confirm
that RDDs produce negative effects more frequently than OLS regressions.

Why is there no clear-cut evidence in favour or against the "law of $1/n$"? A
plausible reason may be that there are few incentives for the pure accumulation
of knowledge in the social sciences, at least when compared to the benefits
scholars may accrue when they challenge or add features to existing theories
[@geddes2003paradigms]. This leads to a reduced number of replication studies in
the field, although we have seen some positive changes in this respect, such as
EGAP's _Metaketa Initiative_.\footnote{See
\url{https://egap.org/our-work/the-metaketa-initiative} for further
information.} For instance, in our sample, papers added supermajority rules
[@lee2015supermajority; @lee2016supermajority], redistricting
[@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact],
coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits],
bicameralism [@ricciuti2004legislature], and the interplay between upper and
lower houses [@chen_malhotra_2007] to the main theory, but a comprehensive
procedural replication of the findings using different samples is yet to be
written. The addition of new features has the benefit of enriching the original
theory with useful details, although it has the disadvantage of not providing a
conclusive test to the "law of $1/n$".

Our analyses suggest three areas for further research. First, our study
sample did not include articles that evaluate the association between the
log($n$) and public expenditure per capita or between $k$ and log expenditure
per capita. New work on that area might clarify some of the inconsistencies we
find here. Second, despite the inclusion of several moderators in our models,
aggregate results still show considerable heterogeneity. Domestic factors such
as party dynamics or gerrymandering [@lee2015supermajority;
@mukherjee2003politicalparties; @gilligan2006public] may prove useful in this
regard. Finally, we highlight the need for more causal inference studies in the
literature. Whenever possible, authors should leverage natural and
quasi-experiments to assess whether the current results hold when tested with
such research designs. These suggestions may help scholars and policy-makers to
reach an optimal balance between sound fiscal policy and the demands for
increased political representation.

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

\nocite{baskaran2013coalition, bradbury2009spatially, drew2017price,
erler2007termlimits, fiorino2007legislature, hohmann2017effect,
kessler2014communication, lewis2019legislature, lledo2003electoral,
mukherjee2003politicalparties, petterssonlidbom2012size, schaltegger2009large,
stein1998institutional, mukherjee2003politicalparties, macdonald2008impact,
matsusaka2005endogeneity, ricciuti2004legislatures}

