---
title:  |
        | The Effect of Legislature Size on Public Spending:
        | A Meta-Analysis
author: 
  - Huzeyfe Alptekin[^huzeyfe]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
  - Catarina Roman[^catarina]
date: \today
thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at <https://github.com/danilofreire/distributive-politics-meta-analysis>. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending. Based on a sample of 29 articles, we find no robust evidence for the effect of legislature size on government budgets. Yet the aggregate results show significant heterogeneity. While earlier studies provide moderate support for the \"law of $1/n$\", papers using causal inference methods consistently find a negative relationship between seats and spending. The available evidence also indicates that proportional representation and mixed voting systems are no more likely to overspend than majoritarian ones."
abstractspacing: double
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Clean up
rm(list = ls())

## Starting
set.seed(732578) # From random.org

# Needed packages
pkgs <- c("tidyverse", "meta", "metafor",
          "readxl", "data.table",
          "knitr", "gridGraphics", "gridExtra",
          "ggpubr", "kableExtra", "magick")

# Install if not already installed
installIfNot <- function(x) {
  if (x %in% rownames(installed.packages()) == FALSE)
    install.packages(x, dependencies = T,
					 repos = "http://cran.us.r-project.org")
}
lapply(pkgs, installIfNot)

# Load packages
lapply(pkgs, require, character.only = T)
devtools::install_github("isubirana/compareGroups")
library("compareGroups")

# Load datasets
load("../dataset/dataCoefs.RData")

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(mod$lower.random,
                          mod$lower.predict),
                upper = c(mod$upper.random,
                          mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()

  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

# Build forest plot for heterogeneous analysis
# Build plot function for forest plots
build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod <- update(mod, byvar = hetvar, print.byvar = F)
  
  # Build dataset for plot
  mod2 <- tibble(
    byvar = mod$byvar,
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    arrange(byvar)
  auxmod <- tibble()
  for (i in rev(mod$bylevs)){
    auxmod <- rbind(auxmod, tibble(byvar = i,
                    TE = NA,
                    seTE = NA,
                    studlab = toupper(i),
                    lower = NA,
                    upper = NA,
                    group = "B"))
    auxmod <- rbind(auxmod, 
                    filter(mod2, byvar==i) %>% 
                      arrange(desc(TE)))
    auxmod <- rbind(auxmod, tibble(
      byvar = i,
      TE = mod$TE.random.w[which(mod$bylevs==i)],
      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
      studlab = 'Subgroup Effect',
      lower = mod$lower.random.w[which(mod$bylevs==i)],
      upper = mod$upper.random.w[which(mod$bylevs==i)],
      group = "B"))
  }
  auxmod <- rbind(auxmod, tibble(
    byvar = NA,
    TE = c(mod$TE.random, NA),
    seTE = c(mod$seTE.random, NA),
    studlab = c("Overall Effect", "Prediction Interval"),
    lower = c(mod$lower.random, mod$lower.predict),
    upper = c(mod$upper.random, mod$upper.predict),
    group = "B"))
  mod2 <- data.frame(auxmod)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
  
  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))
  
  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}
```

[^huzeyfe]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.

[^catarina]: PhD Student, Department of Political Science, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

\newpage

# Introduction
\label{sec:intro}

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Most
early studies that empirically tested the "law of $1/n$", as the theory is
currently known, indeed found a positive correlation between the number of
legislature seats and different measures of government spending, although the
effect was often limited to one house [e.g., @baqir2002districting;
@gilligan1995deviations; @gilligan2001fiscal]. Recent research has further
questioned the validity of the "law of $1/n$". For instance, spending limits,
bicameralism, or strong executives may reduce the inefficiency of pork barrel
projects [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop].
Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending. 

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Given this diversity of empirical
findings, a systematic review of the existing evidence may help us reach a
meaningful conclusion about the effect of legislature size on public spending.
Meta-analysis is the most appropriate method for this task. Meta-analysis
combines the outcomes of multiple studies into a single estimation and allows
scholars to draw robust conclusions from the aggregated data
[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy].

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that
use quantitative methods to assess the impact of legislature size over
government spending across several dimensions. We run two sets of models: the
first group uses only the main estimates of each selected paper (`r dim(dat)[1]`),
while the second set includes all coefficients reported in our
sample (`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))`
papers in our review, we include `r dim(dat)[1]` coefficients in the restricted 
sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles 
report separate estimates for the impact of lower and upper house size on 
government expenditures. In the full model, we add every outcome reported in the 
papers, regardless of whether the coefficient comes from the main tables or from 
robustness checks. We discuss our sampling process in the Methods section and in 
the Supplementary Material.}
Our independent variables consist of three measures, namely the size of the
lower chamber ($n$), its natural logarithm (log($n$)), and the number of members
in the upper chamber ($k$). We evaluate their effect upon public expenditure per
capita, the natural logarithm of public expenditure per capita, and government
expenditure as a percentage of GDP. We then estimate if the results vary
according to four potential sources of effect heterogeneity.

Aggregate results show that legislative size has no significant impact on
public spending. However, the meta-regressions suggest that our study sample
has high levels of heterogeneity, and effects differ substantially according to
study specifications. We find that one reliable predictor of effect size is the
research method employed in the original paper. While papers that employ
conventional linear regressions often find a positive relation between
legislature size and government budgets, recent studies using modern methods of
causal inference, specially those with regression discontinuity designs,
provide consistent evidence for a negative relation. This goes in contrast with
the original theory and supports the existence of a "reverse law of $1/n$".
Additionally, we find that non-majoritarian voting systems decrease government
spending as a percentage of GDP, which is also evidence against the theoretical
expectations of the "law of $1/n$", and they do not have a relevant impact on
the other measures of public expenditure. In summary, our analysis does not
provide robust support for the theory as originally conceived, and causal
inference models suggest that larger legislatures are associated with lower
public spending.


# Data and Methods

We compiled our study sample in three rounds. In the first search round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that cited
\citet{weingast1981political}, as it is the foundational work in the literature
on the "law of $1/n$". We then restricted our query to articles written in
English and, to ensure that studies were comparable, we only included papers
that used quantitative methods to investigate the relationship between
legislature size and public spending\footnote{Please refer to Section C in the
Supplementary Material for a detailed description of the selection procedure.
We include two PRISMA (Preferred Reporting Items for Systematic Reviews and
Meta-Analyses) flow diagrammes \citep{liberati2009prisma} showing the number of
resulting papers after each review step.}. After this stage, we identified the
variables authors most commonly employ to measure government expenditure and
legislature size, our dependent and independent variables, respectively. For
government expenditure, our study sample uses (i) public expenditure as a share
of GDP; (ii) public expenditure per capita; and (iii) the natural logarithm of
public expenditure per capita as its main variables of interest\footnote{Since
meta-analysis requires a single estimate per observation, we excluded articles
that use interaction terms or quadratic specifications of our selected
variables.}. In regards to legislature size, the variables are (i) lower
chamber size; (ii) natural logarithm of lower chamber size; and (iii) upper
house size\footnote{There are a few important nuances concerning coding of
these variables. For instance, unicameralism is captured both by lower chamber
size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the
literature estimates how institutional designs affect this relationship, ours
and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any articles that used the natural
logarithm of upper chamber size.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. We again restricted the search to articles written in English
which employed quantitative methods. In the third search round, we looked into
the personal webpages of every author we had already included in our previous
sample. The purpose of this manual search was to assess whether there was any
working paper or unpublished manuscript which we might had missed in the
previous queries. All papers we found in that last search had already been
included in our sample. Combined, the three searches produced a dataset of 
`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March,
2021. Table \ref{tab:papers} contains the full list of articles we analyse in
this paper.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Journals: Unpub$=$Unpublished, JPE$=$Journal of
Political Economy, EJPE$=$European Journal of Political Economy, PC$=$Public
Choice, JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private
Enterprise, APSR$=$American Political Science Review, SEJ$=$Southern Economic
Journal, UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative
International Development, SSQ$=$Social Science Quarterly, SPPQ$=$State
Politics and Policy Quarterly, CPS$=$Comparative Political Studies,
RivPE$=$Rivista di Politica Economica, E\&P$=$Economics and Politics,
NTJ$=$National Tax Journal. Country codes follow the ISO 3166-1 alpha-3
international standard. Dependent variable: ExpPC$=$Per capita expenditure,
logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as
a percentage of GDP. Method: OLS$=$Ordinary least squares, IV$=$Instrumental
variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity
design. Electoral system: M$=$Majoritarian, NM$=$Non-majoritarian (mixed or
proportional representation).} 
\end{minipage} 
\end{longtable}

\normalsize

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Eight articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, while studies from 2012 onward have also applied causal inference designs,
such as instrumental variables and regression discontinuity models.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
and tested the impact of larger legislatures on different measures of government
spending. Our independent variables of interest are lower chamber size 
(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded five moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study. The
additional moderators are: 1) publication year; 2) paper publication in an
academic journal; 3) estimation method; 4) institutional design; 5) electoral
system. Since the literature on the "law of $1/n$" is notably diverse, we
included only moderators that either refer to important theoretical questions,
such as the effect of the electoral system on public spending, or to essential
characteristics of the publications themselves. Although more moderators exist
in the literature (e.g., data aggregation level), they do not appear as often
as necessary for their inclusion in the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables. 

\vspace{.5cm}

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```
\normalsize

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets, and almost all papers fit more
than one model with similar variables, what suggests that the assumption does
not hold. We use two procedures to tackle this problem. First, we created two
sets of study coefficients to reduce the impact of multicollinearity in our
estimations. The first group includes only the most rigorous models from each
paper, that is, those estimated with the largest $n$, most control variables,
and fixed effects if the authors added them. If the article employed a
regression discontinuity design, we chose the coefficient from the optimal
bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]`
estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed
two dependent or independent variables of interest\footnote{The papers that
used more than one dependent or independent variable of interest are
\citet{baqir1999districts, bjedov2014impact, bradbury2001legislative,
chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in
contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the 
`r length(unique(dat$id))` papers. Here we focus on the results for our restricted
sample as we consider them more robust, but the findings are very similar when
we use the extended set.

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another indicating the data source used in the original
study. By adding these two levels, we account for within- and between-study
variation, thus removing these sources of effect size dependency. More
information about the multilevel models can be found in Section H of the
Supplementary Material. 

# Discussion
\label{sec:discussion}

In this letter, we assess the empirical validity of the "law of $1/n$". Based
on a sample of `r length(unique(dat$id))` publications on the topic, our
meta-analyses show that there is no strong evidence that an increase in the
number of legislators has a significant effect on public expenditures. If such
effect exists, it is likely driven by an increase in $k$, the size of the upper
legislature, as suggested by several studies in the literature
[@baqir2002districting; @bradbury2001legislative; @bradbury2003local;
@chen_malhotra_2007; @gilligan2001fiscal; @primo2006stop]. Instead, we find
better evidence for the "reverse law of $1/n$", which posits that larger
legislatures lead to lower government spending. This is mainly because studies
using regression discontinuity designs, a method that has robust internal
validity, consistently indicate a negative relationship between lower house size
and the logarithm of expenditure per capita [@hohmann2017effect;
@lewis2019legislature; @petterssonlidbom2012size].

The meta-regressions show that study characteristics have a considerable
influence on reported results. Electoral system affects the relationship
between legislature size and public expenditure, but the results are not
replicable in all estimations. Publication year generates conflicting findings
in our models. Nevertheless, the meta-regressions confirm that RDDs produce
negative effects more frequently than OLS regressions.

Why is there no clear-cut evidence in favour or against the "law of $1/n$"? A
plausible reason may be that there are few incentives for the pure accumulation
of knowledge in the social sciences, at least when compared to the benefits
scholars may accrue when they challenge or add features to existing theories
[@geddes2003paradigms]. This leads to a reduced number of replication studies in
the field, although we have seen some positive changes in this respect, such as
EGAP's _Metaketa Initiative_.\footnote{See
\url{https://egap.org/our-work/the-metaketa-initiative} for further
information.} For instance, in our sample, papers added supermajority rules
[@lee2015supermajority; @lee2016supermajority], redistricting
[@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact],
coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits],
bicameralism [@ricciuti2004legislature], and the interplay between upper and
lower houses [@chen_malhotra_2007] to the main theory, but a comprehensive
procedural replication of the findings using different samples is yet to be
written. The addition of new features has the benefit of enriching the original
theory with useful details, although it has the disadvantage of not providing a
conclusive test to the "law of $1/n$".

Our analyses suggest three areas for further research. First, our study
sample did not include articles that evaluate the association between the
log($n$) and public expenditure per capita or between $k$ and log expenditure
per capita. New work on that area might clarify some of the inconsistencies we
find here. Second, despite the inclusion of several moderators in our models,
aggregate results still show considerable heterogeneity. Domestic factors such
as party dynamics or gerrymandering [@lee2015supermajority;
@mukherjee2003politicalparties; @gilligan2006public] may prove useful in this
regard. Finally, we highlight the need for more causal inference studies in the
literature. Whenever possible, authors should leverage natural and
quasi-experiments to assess whether the current results hold when tested with
such research designs. These suggestions may help scholars and policy-makers to
reach an optimal balance between sound fiscal policy and the demands for
increased political representation.

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

\nocite{baskaran2013coalition, bradbury2009spatially, drew2017price,
erler2007termlimits, fiorino2007legislature, hohmann2017effect,
kessler2014communication, lewis2019legislature, lledo2003electoral,
mukherjee2003politicalparties, petterssonlidbom2012size, schaltegger2009large,
stein1998institutional, mukherjee2003politicalparties, macdonald2008impact,
matsusaka2005endogeneity, ricciuti2004legislatures}


