---
title:  |
        | The Effect of Legislature Size on Public Spending
        | A Meta-Analysis
author: 
  - Huzeyfe Alptekin[^huzeyfe]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
  - Catarina Roman[^catarina]
date: \today
thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at <https://github.com/danilofreire/distributive-politics-meta-analysis>. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending. Based on a sample of 29 articles, we find no robust evidence for the effect of legislature size on government budgets. Yet the aggregate results show significant heterogeneity. While earlier studies provide moderate support for the \"law of $1/n$\", papers using causal inference methods consistently find a negative relationship between seats and spending. The available evidence also indicates that proportional representation and mixed voting systems are no more likely to overspend than majoritarian ones."
abstractspacing: double
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Clean up
rm(list = ls())

## Starting
set.seed(732578) # From random.org

# Needed packages
pkgs <- c("tidyverse", "meta", "metafor",
          "readxl", "data.table",
          "knitr", "gridGraphics", "gridExtra",
          "ggpubr", "kableExtra", "magick")

# Install if not already installed
installIfNot <- function(x) {
  if (x %in% rownames(installed.packages()) == FALSE)
    install.packages(x, dependencies = T,
					 repos = "http://cran.us.r-project.org")
}
lapply(pkgs, installIfNot)

# Load packages
lapply(pkgs, require, character.only = T)
devtools::install_github("isubirana/compareGroups")
library("compareGroups")

# Load datasets
load("../dataset/dataCoefs.RData")

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(mod$lower.random,
                          mod$lower.predict),
                upper = c(mod$upper.random,
                          mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()

  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

# Build forest plot for heterogeneous analysis
# Build plot function for forest plots
build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod <- update(mod, byvar = hetvar, print.byvar = F)
  
  # Build dataset for plot
  mod2 <- tibble(
    byvar = mod$byvar,
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    arrange(byvar)
  auxmod <- tibble()
  for (i in rev(mod$bylevs)){
    auxmod <- rbind(auxmod, tibble(byvar = i,
                    TE = NA,
                    seTE = NA,
                    studlab = toupper(i),
                    lower = NA,
                    upper = NA,
                    group = "B"))
    auxmod <- rbind(auxmod, 
                    filter(mod2, byvar==i) %>% 
                      arrange(desc(TE)))
    auxmod <- rbind(auxmod, tibble(
      byvar = i,
      TE = mod$TE.random.w[which(mod$bylevs==i)],
      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
      studlab = 'Subgroup Effect',
      lower = mod$lower.random.w[which(mod$bylevs==i)],
      upper = mod$upper.random.w[which(mod$bylevs==i)],
      group = "B"))
  }
  auxmod <- rbind(auxmod, tibble(
    byvar = NA,
    TE = c(mod$TE.random, NA),
    seTE = c(mod$seTE.random, NA),
    studlab = c("Overall Effect", "Prediction Interval"),
    lower = c(mod$lower.random, mod$lower.predict),
    upper = c(mod$upper.random, mod$upper.predict),
    group = "B"))
  mod2 <- data.frame(auxmod)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
  
  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))
  
  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}
```

[^huzeyfe]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.

[^catarina]: PhD Student, Department of Political Science, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

\newpage

# Introduction
\label{sec:intro}

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Most
early studies that empirically tested the "law of $1/n$", as the theory is
currently known, indeed found a positive correlation between the number of
legislature seats and different measures of government spending, although the
effect was often limited to one house [e.g., @baqir2002districting;
@gilligan1995deviations; @gilligan2001fiscal]. Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending. Recent research has further
questioned the validity of the "law of $1/n$". Since the wide range of empirical tests has produced conflicting results, scholars began to target the theoretical foundations of the law. Authors such as @crowley2019law and @pecorino2018supermajority accurately point out that collective action problems have been overlooked, but their expanded models cannot account for all the institutional variation previous studies explore.

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We select `r length(unique(dat$id))` articles that
use quantitative methods to assess the impact of legislature size over
government spending across several dimensions. Out 
of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Although other studies aimed at solving this inconsistency, meta-analysis is the most appropriate tool, as it combines multiple outcomes into a single estimation and allows
us to draw robust conclusions from the aggregated data [@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy]. 

We believe the scrutiny of the law expanded its initial scope in two directions. One group of scholars investigates the original institutional framework for the presence of coalitions, supermajorities, veto powers, and spending limits, which the theory disregards. They suggest these dynamics strongly influence the $1/n$ effect -- specifically in U.S. majoritarian local legislatures, for which the law was conceived. Another sector of the scholarship overrides this institutional context. They find that the different political arrangements in national congresses, State legislatures, regional European governments, etc. produce more nuanced results. For instance, intergovernmental competition, the size ratio between assemblies, and strong executives demonstrated the effect of legislative size on public spending could be non-linear, asymmetrical, and even negative. While these trends evolved, causal inference tools became more sophisticated, allowing this inquiry to grow also in roubstness. We address all of these developments in this study. We coded five different moderators that translate methodological advances in time, the similarity of the empirical cases to the original @weingast1981political framework, and key theoretical issues to identify sources of variation in the literature.

Aggregate results show that legislative size has no significant impact on
public spending. Our meta-analysis estimates are exactly half positive, and half negative. 
Meta-regressions suggest that our study sample is highly heterogeneous, and effects differ substantially according to study specifications. In the broadest aggregation models, unicameralism supports the positive effect predicted by the 
law of $1/n$. Since most unicameral cases in our sample refer to local governments (municipalities or districts), this result supports the theory strictly in its original institutional framework. It also indirectly endorses studies that find odd results in bicameralism. As follows, meta-regressions confirm previous findings that larger upper chambers spend more in terms of per capita expenditure than lower chambers [@gilligan1995deviations; @gilligan2001fiscal]. 
Moreover, non-majoritarian voting systems decrease government spending as a percentage of GDP, and they do not have a relevant impact on the other measures of public expenditure, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original formulation of the law.

The meta-regressions also indicate that the $1/n$ effect found in earlier studies might be sensitive to more robust estimation methods. While papers that employ conventional linear regressions often find a positive relation between
legislature size and government budgets, recent studies using modern methods of
causal inference, specially those with regression discontinuity designs,
provide consistent evidence for a negative relation [@crowley2019law; @debenedetto2018; @hohmann2017effect; @lewis2019legislature]. This goes in contrast with
the original theory and supports the existence of a "reverse law of $1/n$". In summary, our results are in line 
with previous findings that lend partial support to the law of $1/n$ 
[@chen2007law; @crowley2015local; @primo2006stop]. An assessment of the effects of collective action costs in these analyses is crucial to determine the full mechanism operating behind these results. Overall, our analysis does not
provide robust support for the theory as originally conceived. 


# Methods

We compiled our study sample in three rounds. In the first search round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that cited
\citet{weingast1981political}, as it is the foundational work in the literature
on the "law of $1/n$". We then restricted our query to articles written in
English and, to ensure that studies were comparable, we only included papers
that used quantitative methods to investigate the relationship between
legislature size and public spending\footnote{Please refer to Section C in the
Supplementary Material for a detailed description of the selection procedure.
We include two PRISMA (Preferred Reporting Items for Systematic Reviews and
Meta-Analyses) flow diagrammes \citep{liberati2009prisma} showing the number of
resulting papers after each review step.}. After this stage, we identified the
variables authors most commonly employ to measure government expenditure and
legislature size, our dependent and independent variables, respectively. For
government expenditure, our study sample uses (i) public expenditure as a share
of GDP; (ii) public expenditure per capita; and (iii) the natural logarithm of
public expenditure per capita as its main variables of interest\footnote{Since
meta-analysis requires a single estimate per observation, we excluded articles
that use interaction terms or quadratic specifications of our selected
variables.}. In regards to legislature size, the variables are (i) lower
chamber size; (ii) natural logarithm of lower chamber size; and (iii) upper
house size\footnote{There are a few important nuances concerning coding of
these variables. For instance, unicameralism is captured both by lower chamber
size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the
literature estimates how institutional designs affect this relationship, ours
and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any articles that used the natural
logarithm of upper chamber size.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. We again restricted the search to articles written in English
which employed quantitative methods. In the third search round, we looked into
the personal webpages of every author we had already included in our previous
sample. The purpose of this manual search was to assess whether there was any
working paper or unpublished manuscript which we might had missed in the
previous queries. All papers we found in that last search had already been
included in our sample. Combined, the three searches produced a dataset of 
`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March,
2021. Table \ref{tab:papers} contains the full list of articles we analyse in
this paper.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Notre:} Country codes
follow the ISO 3166-1 alpha-3 international standard.}
\footnotetext{\textbf{Journals:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Methods:} 
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation).} 
\footnotetext{\textbf{Dependent Variables:} ExpPC$=$Per capita expenditure, logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as a percentage of GDP.}\end{minipage}
\end{longtable}

\normalsize

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Eight articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, while studies from 2012 onward have also applied causal inference designs,
such as instrumental variables and regression discontinuity models.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
and tested the impact of larger legislatures on different measures of government
spending. Our independent variables of interest are lower chamber size 
(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded five moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study. The
additional moderators are: 1) publication year; 2) paper publication in an
academic journal; 3) estimation method; 4) institutional design; 5) electoral
system. Since the literature on the "law of $1/n$" is notably diverse, we
included only moderators that either refer to important theoretical questions,
such as the effect of the electoral system on public spending, or to essential
characteristics of the publications themselves. Although more moderators exist
in the literature (e.g., data aggregation level), they do not appear as often
as necessary for their inclusion in the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables. 

\vspace{.5cm}

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```
\normalsize

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets, and almost all papers fit more
than one model with similar variables, what suggests that the assumption does
not hold. We use two procedures to tackle this problem. First, we created two
sets of study coefficients to reduce the impact of multicollinearity in our
estimations. The first group includes only the most rigorous models from each
paper, that is, those estimated with the largest $n$, most control variables,
and fixed effects if the authors added them. If the article employed a
regression discontinuity design, we chose the coefficient from the optimal
bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]`
estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed
two dependent or independent variables of interest\footnote{The papers that
used more than one dependent or independent variable of interest are
\citet{baqir1999districts, bjedov2014impact, bradbury2001legislative,
chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in
contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the 
`r length(unique(dat$id))` papers. Here we focus on the results for our restricted
sample as we consider them more robust, but the findings are very similar when
we use the extended set.

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another indicating the data source used in the original
study. By adding these two levels, we account for within- and between-study
variation, thus removing these sources of effect size dependency. More
information about the multilevel models can be found in Section H of the
Supplementary Material. 

# Results

Resumir resultados das meta-análises.
Incluir regressões com todos os coeficientes na tabela de meta-regressions.
Incluir frases com "highlights" na sub-seção de meta-regressions.
Trocar parágrafo introdutório e o de binomial z-tests pela nova versão do Danilo (que não subiu pro repo).

## Binomial Z-Tests
\label{sub:binomial}

The "law of $1/n$" states that more legislators increase government expenditure.
Here we employ three methods to assess the empirical validity of that
relationship. First, we run a binomial one-proportion z-test to determine
whether the study coefficients have a positive or negative sign. Then, we fit 9
random-effect models using the \texttt{meta} \citep{balduzzi2019perform} and the
\texttt{dmetar} \citep{dmetar2019} packages for the \texttt{R} statistical
language \citep{rstats2019}. We estimate the true effect size variance
($\tau^2$) with a Restricted Maximum Likelihood Estimator, which the literature
considers the most precise for continuous dependent variables
\citep{veroniki2016methods}. Lastly, we run a series of meta-regressions to test
possible sources of result heterogeneity. To recapitulate, our independent
variables of interest are lower chamber size, the natural logarithm of
lower chamber size, and upper chamber size. The dependent
variables are public expenditure per capita, the natural logarithm of public
expenditure per capita, and government expenditure as a percentage of GDP. Since
the outcomes have different scales, we treat them separately in our models.

```{r, cache=TRUE, echo = FALSE}
aux <- filter(dat, indepvar2 == "N")
binN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux <- filter(dat, indepvar2=='K')
binK <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux <- filter(dat, indepvar2 == "logN")
binlogN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
```

The binomial z-test evaluates whether the coefficient of our independent
variables are positive or negative. The null hypothesis here states that the
sign of the coefficient is equally likely to be positive or negative. We start
with lower house size. Our results indicate that there is no correlation
between the number of legislators in the lower house and public expenditure 
(successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
association between both. The binomial test for the natural logarithm of lower chamber size also shows a
non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
positive result for the number of legislators in the upper house, which is
in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binK$p.value), 3)`). 

## Meta-Analysis
\label{sub:Meta-Analysis}

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the 9 possible variable combinations, we found only 7 in
the article pool. Our sample includes no papers that analyse the relationships
between the log lower chamber size and public expenditure per capita or between upper chamber size and the
logarithm of public expenditure per capita. We standardized effect sizes by drawing the coefficients and standard errors from the articles. When the latter were not directly available, we used t-statistics to retrieve them. 


```{r, echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE}
mod <- list()
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod[[1]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod[[2]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod[[3]] <- metagen(
  coef, SE, data=aux,
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction = TRUE,
  sm="SMD"
  )

# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

mod[[4]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod[[5]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

mod[[6]] <- metagen(
  coef, SE, data=aux,
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction=TRUE,
  sm="SMD"
  )

# Pooling effects analysis -- PCTGDP x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

mod[[7]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Full model - Pooling effects analysis -- PCTGDP x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod[[8]] <- metagen(coef, SE, data = aux,
          studlab = paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm = "SMD")


# Full data - Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod[[9]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
```

\begin{landscape}
\begin{figure}[htb]
\begin{center}
\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
\vspace{.3cm}
\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
\label{fig:plots}
\end{center}
\end{figure}
\end{landscape}

Figure \ref{fig:plots} shows the forest plots for our restricted sample,
which includes only the `r dim(dat)[1]` main coefficients of the 
`r length(unique(dat$id))` selected papers. On the left side of the plots are 
the name of the study authors and the paper publication year. For unpublished
studies, we included the first year the paper was available online. The bars in
the middle show the reported effect sizes and the vertical lines indicate their
average, weighted by standard errors. The length of the lines represent the
precision of the estimates. The red line at the bottom of the figures displays
the aggregate coefficients plus their respective confidence intervals.

The first line of graphs reports the results for lower chamber size.
In the first model, which correlates lower chamber size and expenditure per capita, we find a
standardised mean difference (SMD) of `r round(mod[[1]]$TE.random,3)` and a standard error of `r round(mod[[1]]$seTE.random,3)`
(studies = `r mod[[1]]$k`, 95\% CI = [`r round(mod[[1]]$lower.random,3)`; `r round(mod[[1]]$upper.random,3)`], $p$-value = `r round(mod[[1]]$pval.random,3)` , prediction interval
= [`r round(mod[[1]]$lower.predict,3)`; `r round(mod[[1]]$upper.predict,3)`]). Therefore, we cannot reject the null hypothesis that the
effect size is zero. The $I^2$ statistic, which quantifies the degree of
heterogeneity among studies, is equal to `r round(mod[[1]]$I2*100, 2)`\%. $I^2$ values above 75\%
indicate very high study heterogeneity [@higgins2019cochrane].

We see similar results when we compare lower chamber size with log expenditure per capita. In
this model, the average effect size is `r round(mod[[3]]$TE.random,3)` and the standard error is
`r round(mod[[3]]$seTE.random,3)` (studies = `r mod[[3]]$k`, 95\% CI = [`r round(mod[[3]]$lower.random,3)`; `r round(mod[[3]]$upper.random,3)`], $p$-value = `r round(mod[[3]]$pval.random,3)`, prediction
interval = [`r round(mod[[3]]$lower.predict,3)`; `r round(mod[[3]]$upper.predict,3)`]; $I^2$ = `r round(mod[[3]]$I2*100, 2)`\%). The coefficient is 
statistically indistinguishable from zero.

In our restricted sample, larger lower house size also does not increase
government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD = `r round(mod[[5]]$TE.random,3)`, SE =
`r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
[`r round(mod[[5]]$lower.predict,3)`; `r round(mod[[5]]$upper.predict,3)`], $I^2$ = `r round(mod[[5]]$I2*100, 2)`\%). In the extended sample the effect is negative, but it is also statistically insignificant.

XXXXX We find a positive effect in our extended
sample and the coefficient is statistically significant at the 10\% level
(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; #`r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
result supports the "law of 1/$n$", but the evidence is moderate
as the prediction interval include zero.

Next, we present the meta-analyses using the logarithm of lower house
size. We start with the relationship between
this variable and the logarithm of expenditure per capita. The result is positive, but the coefficient is not significant, and the prediction interval encompasses zero
(studies = `r mod[[4]]$k`, SMD = `r round(mod[[4]]$TE.random,3)`, SE = `r round(mod[[4]]$seTE.random,3)`, 95\% CI = [`r round(mod[[4]]$lower.random,3)`; `r round(mod[[4]]$upper.random,3)`], $p$-value =
`r round(mod[[4]]$pval.random,3)`, prediction interval = [`r round(mod[[4]]$lower.predict,3)`; `r round(mod[[4]]$upper.predict,3)`], $I^2$ = `r round(mod[[4]]$I2*100, 2)`\%). Results in the full sample are also null.

Our model that correlates log lower chamber size with public expenditures as a percentage of
GDP fails to reach conventional levels of statistical significance (studies =
`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = `r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`; `r round(mod[[6]]$upper.random,3)`], $p$-value = `r round(mod[[6]]$pval.random,3)`,
prediction interval = [`r round(mod[[6]]$lower.predict,3)`; `r round(mod[[6]]$upper.predict,3)`], $I^2$ = `r round(mod[[6]]$I2*100, 2)`\%). The extended sample
also gives us a null result.

The third set of models uses upper house size as the main independent
variable. We find a positive correlation between this variable and expenditure per capita
but the coefficient is not significant (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
= `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
[`r round(mod[[2]]$lower.predict,3)`; `r round(mod[[2]]$upper.predict,3)`], $I^2$ = `r round(mod[[2]]$I2*100, 2)`\%). But as with the other models, the prediction
interval again includes zero. When we run the same analysis in the extended
sample, we see a significant coefficient for the estimate, yet the prediction interval also
contains zero (coefficients = `r mod[[9]]$k`, SMD = `r round(mod[[9]]$TE.random,3)`, SE = `r round(mod[[9]]$seTE.random,3)`, 95\% CI = [`r round(mod[[9]]$lower.random,3)`; `r round(mod[[9]]$upper.random,3)`],
$p$-value $<$ 0.001, prediction interval = [`r round(mod[[9]]$lower.predict,3)`; `r round(mod[[9]]$upper.predict,3)`], $I^2$ = `r round(mod[[9]]$I2*100, 2)`\%).

Our last estimation analyses the relationship between upper chamber size and government
spending as a percentage of GDP. The coefficient is not statistically
significant, indicating a null effect (studies = `r mod[[7]]$k`, SMD = `r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI
= [`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`], $p$-value = `r round(mod[[7]]$pval.random,3)`, prediction interval = [`r round(mod[[7]]$lower.predict,3)`; `r round(mod[[7]]$upper.predict,3)`],
$I^2$ = `r round(mod[[7]]$I2*100, 2)`\%). The result is very similar in the extended sample.

In a nutshell, we do not find strong evidence in favour of the "law of $1/n$".
While some models do show a positive and statistically significant result, none
of the prediction intervals are totally positive or negative. The studies also
have considerable heterogeneity, what indicates that the original coefficients
do not point consistently towards the same direction.

One reason why we have not detected any strong effects may be due to the
identification strategy authors use in their models. On the one hand, OLS and
panel data models require too many controls to make units comparable, and they
are vulnerable to omitted variable bias or post-treatment bias
[@cinelli2020making; @pearl2015conditioning]. On the other hand, estimation
methods such as instrumental variables and regression discontinuity designs
have become popular because of their high internal validity
[@angrist2008mostly]. Figure \ref{fig:plots2} shows the disaggregated effects
for two sets of models that employ causal estimation techniques. They measure
the impact of lower house size on expenditure per capita (left) and on the
natural logarithm of expenditure per capita (right).

\vspace{.06cm}

\begin{figure}[htb]
\begin{center}
\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (restricted sample)}
\vspace{.3cm}
\includegraphics[width=1\linewidth, height=7.5cm]{../graphs/graph2.pdf}
\label{fig:plots2}
\end{center}
\end{figure}

\newpage 

Papers that employed instrumental variables show some interesting variation: out
of the four coefficients listed, two are positive and two are negative. Two of
these four coefficients are significant, again one positive and one negative.
The subgroup analysis presents a SMD which is negative but insignificant. In
contrast, all papers that use regression discontinuity designs show negative and
statistically significant results. Since only three papers in our sample use
RDDs, we are cautious about predicting an overall negative relation, but they do
indicate that better identification strategies yield a zero-to-negative impact
of legislature size on expenditure, in support of the reverse "law of $1/n$".

## Meta-Regressions
\label{sub:regressions}

In this section, we run a series of meta-regressions with covariates that may
account for differences across the selected papers. The first variable indicates
whether the study uses lower chamber size, log lower chamber size, or upper chamber size as a main explanatory variable. We included the individual effect sizes for upper and lower chamber sizes when papers analyzed both.
The second variable shows the study publication year, which we included to
capture temporal variation in the study coefficients. We also add a dummy
variable to assess whether published articles report effect sizes that are
higher or lower than those from working papers. The fourth variable measures
whether studies focusing on non-majoritarian electoral systems report
coefficients that are smaller or larger than those from majoritarian countries. The fifth covariate is a categorical variable indicating the statistical
procedure used in the original models (panel data, instrumental variables,
OLS, or regression discontinuity design). In our last variable, we separate coefficients that use samples from unicameral or bicameral systems, and code papers using polities with different institutional designs as "mixed".

\newpage 

Table {tabregressions} presents the meta-regression results for our
restricted and extended samples. Each column represents one of the three
measures of public spending we discuss in this paper. To reduce the risk of
false positives in our analyses, we use permutation tests to calculate
significance levels for the meta-regressions \citep{higgins2004controlling}.

The first two models show the results for public expenditure per capita. No
variable reaches conventional levels of statistical significance in the
restricted sample. In the extended sample, we find that models that use lower chamber size as
an independent variable have lower effects when
compared to upper chamber size. This suggests that an additional member in the lower house has
a smaller impact on public spending than a member in the upper house. Moreover,
the results for the extended sample point out that recent studies find larger
effects than older ones.

The third and fourth columns use the natural logarithm of expenditure per capita
as the dependent variable. None of the covariates are statistically significant in our
smaller sample, but two moderators are negatively associated with the outcome in
our larger study pool. They both refer to estimation methods. Studies that
employ panel/fixed effects or regression discontinuity designs (RDDs) have lower
coefficients for log expenditure per capita if we take OLS as the reference
category. 

Two variables are statistically significant in the last set of meta-regressions,
which include public expenditures as a percentage of GDP as the dependent
variable. Both in our restricted and in our extended samples, recent studies
have smaller coefficients than early papers, which stands in contrast with
our previous models. Non-majoritarian voting systems are also
associated with lower levels of public spending, what is against the theoretical
expectations of the "law of $1/n$". The results, however, do not replicate in
the first set of estimations.

Overall, our results suggest that study coefficients are highly sensitive to
research design choices. The same study samples may produce different outcomes
depending on the response variables scholars decide to analyse. Moreover, we
find evidence that results vary considerably if the study employs different
measures of legislature size or use causal research methods. The impact of
factors such as the electoral system or year of publication also appear to be
conditional on the selected model.


# Discussion
\label{sec:discussion}

Discussion:
1 - ok
2 - ok, só corrigir
3 - como nossos resultados "resolvem" as questões da teoria
a linha que avalia o desenho institucional está certa dessa forma.
sobre a galera que escreve sobre as dinâmicas internas de competição e coalisão, podemos inferir que essas dinâmicas influenciam muito mais do que legislature size.
Juntar a lit review com nosso ultimo paragrafo falando sobre as recomendações de para onde deve avançar a literatura. "Apesar de ela ser extensa, vemos que ainda poderiam ser explorados A B C".
4 - ultimo paragrafo vira o que é o terceiro. uma das sugestões é aumentar o numero de replicações, etc, de como a disciplina como um todo deve avançar, sobre como construimos conhecimento na disciplina.

In this article, we assess the empirical validity of the "law of $1/n$". Based
on a sample of `r length(unique(dat$id))` publications on the topic, our
meta-analyses show that there is no strong evidence that an increase in the
number of legislators has a significant effect on public expenditures. If such
effect exists, it is likely driven by an increase in the size of the upper
legislature, as suggested by several studies in the literature
[@baqir2002districting; @bradbury2001legislative; @bradbury2003local;
@chen2007law; @gilligan2001fiscal; @primo2006stop]. Instead, we find
better evidence for the "reverse law of $1/n$", which posits that larger
legislatures lead to lower government spending. This is mainly because studies
using regression discontinuity designs, a method that has robust internal
validity, consistently indicate a negative relationship between lower house size
and the logarithm of expenditure per capita [@hohmann2017effect;
@lewis2019legislature; @petterssonlidbom2012size].

The meta-regressions show that study characteristics have a considerable
influence on reported results. Electoral system affects the relationship
between legislature size and public expenditure, but the results are not
replicable in all estimations. Publication year generates conflicting findings
in our models. Nevertheless, the meta-regressions confirm that RDDs produce
negative effects more frequently than OLS regressions.

The literature explores many mediating and alternative explanations for how or why the number of legislators in a chamber relates to their choice of commmon pool resource use. @crowley2019law argues that a variable that better translates how large legislatures decrease the efficiency of public spending is fragmentation, which also expresses the and that its effect is actually non-linear. Other studies echo this argument and develop other frgamentation mechanisms that explain relationships that are linear and non-linear. For instance, when it comes to district fragmentation, @baqir1999districts and @drew2017price support the "law of $1/n$"'s positive effect on public spending when one considers the amount of districts that share a common pool of resources. Many studies demonstrate how partisan fragmentation is a bigger predictor of increased spending, and analyze how majorities and veto powers respectively boost and curtail these effects [@baqir2002districting, cite all the papers]. These findings dialogue directly with @weingast1981political's *norm of universalism* within US legislatures, which is the assumption that, when drawing from common pool resources, chambers will always approve of any singular legislators' projects. 

Applying the "law of $1/n$" in contexts too far removed from the US attests against it, as, for instance, public spending more strongly correlates to cabinet than legislature size in Swiss cantons and Malaysian (states or municipalities?), where decision-making power is concentrated in the executive.


Why is there no clear-cut evidence in favour or against the "law of $1/n$"? A
plausible reason may be that there are few incentives for the pure accumulation
of knowledge in the social sciences, at least when compared to the benefits
scholars may accrue when they challenge or add features to existing theories
[@geddes2003paradigms]. This leads to a reduced number of replication studies in
the field, although we have seen some positive changes in this respect, such as
EGAP's _Metaketa Initiative_.\footnote{See
\url{https://egap.org/our-work/the-metaketa-initiative} for further
information.} 

For instance, in our sample, papers added supermajority rules
[@lee2015supermajority; @lee2016supermajority], redistricting
[@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact],
coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits],
bicameralism [@ricciuti2004legislature], and the interplay between upper and
lower houses [@chen2007law] to the main theory, but a comprehensive
procedural replication of the findings using different samples is yet to be
written. 

The addition of new features has the benefit of enriching the original
theory with useful details, although it has the disadvantage of not providing a
conclusive test to the "law of $1/n$".

Our analyses suggest three areas for further research. First, our study
sample did not include articles that evaluate the association between the
log lower chamber size and public expenditure per capita or between upper chamber size and log expenditure
per capita. New work on that area might clarify some of the inconsistencies we
find here. Second, despite the inclusion of several moderators in our models,
aggregate results still show considerable heterogeneity. Domestic factors such
as party dynamics or gerrymandering [@lee2015supermajority;
@mukherjee2003politicalparties; @gilligan2006public] may prove useful in this
regard. Finally, we highlight the need for more causal inference studies in the
literature. Whenever possible, authors should leverage natural and
quasi-experiments to assess whether the current results hold when tested with
such research designs. These suggestions may help scholars and policy-makers to
reach an optimal balance between sound fiscal policy and the demands for
increased political representation.

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

\nocite{baskaran2013coalition, bradbury2009spatially, drew2017price,
erler2007termlimits, fiorino2007legislature, hohmann2017effect,
kessler2014communication, lewis2019legislature, lledo2003electoral,
mukherjee2003politicalparties, petterssonlidbom2012size, schaltegger2009large,
stein1998institutional, mukherjee2003politicalparties, macdonald2008impact,
matsusaka2005endogeneity, ricciuti2004legislatures}

