---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
output:
  pdf_document:
    keep_tex: true
---

```{=latex}
\tableofcontents
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Search criteria

### Search terms

XXXX

### Searched databases

XXXX To Catarina: name and URL of database searched

### Summary total results

XXXX To Catarina: put here results per database, cross-matching, anything else

### Exclusion criteria

#### Exclusion title and abstract

XXXX To Catarina: what criteria for first round exclusions?

#### Exclusion reading

XXXX To Catarina: criteria second round exclusions

#### Exclusion analysis

For the articles that passed the first two filters, we looked into the tables and the reported coefficients. We kept articles in this step based on two criteria:

1. Matched treatment variable:
  + N: Number Legislators Lower House
  + logN: Log Number Legislators Lower House
  + K: Number Legislators Upper House
  
2. Matched outcome variable:
  + ExpPC: Expenditure Per Capita
  + logExpPC: Log Expenditure Per Capita
  + PCTGDP: Percent GDP Public Expenditure


### PRISM

- Number of articles matching the search criteria: XXXX
- Number of articles excluded after title and abstract: XXXX
- Number of articles excluded after reading: XXXX
- Number of articles excluded before analysis: 3
- Number of articles excluded during the analysis: 0

We have 26 articles in the meta-analysis.

## Meta-analysis dataset

The meta-analytic data is comprised of two datasets. The first dataset has the main coefficients that were reported in the paper. XXXX (Copiar da parte de métodos).

## Adding articles

```{r global_options, include=FALSE}
## Starting
set.seed(732578) # From random.org

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
          'dmetar', 'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra','magick')

# Install if not already installed
installIfNot <- function(x) {
  if(x %in% rownames(installed.packages()) == FALSE) 
    install.packages(x, dependencies = T, repos = "http://cran.us.r-project.org")
} 
lapply(pkgs, installIfNot)

# Load packs
lapply(pkgs, require, character.only = T)
rm(pkgs, installIfNot)

# Knitr options
knitr::opts_chunk$set(fig.pos = 'H') # holds figure position

```


```{r, echo=FALSE, include=FALSE}

# Paper 367
dat <- data.frame(
  id = 367,
  published = 'Yes',
  usemeta = 1,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Spatially Targeted Government Spending and
Heterogeneous Constituent Cost Shares',
  author = 'Bradbury and Stephenson',
  year = 2009,
  authoryear = 'Bradbury and Stephenson (2009)',
  journal = 'The Journal of Private Enterprise',
  web = 'http://journal.apee.org/index.php?title=Spring2009_6',
  table = 2,
  column = 2,
  indepvar = 'MEMSENATE',
  indepvar2 = 'K',
  depvar = 'Total Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.624,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.624/3.10
)

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.01262,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.01262/2.12
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 2,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.004964,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.004964/2.9
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 3,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.01134,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.01134/4.52
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 4,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.00559,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.00559/2.39
))

# Paper 585 N
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003627,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.003627/2.51
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 2,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.000517,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.000517/0.47
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 3,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.016946,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.016946/8.65
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 4,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.012337,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.012337/6.65
))

# Paper 505
dat <- rbind(dat,
  data.frame(
  id = 505,
  published = 'Yes',
  usemeta = 1,
  method = 'IV',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The Endogeneity of the Initiative: A Comment on Marschall and Ruhil',
  author = 'Matsusaka',
  year = 2005,
  authoryear = 'Matsusaka (2005)',
  journal = 'State Politics & Policy Quarterly',
  web = 'https://www.jstor.org/stable/40421558',
  table = 1,
  column = 3,
  indepvar = 'Seats',
  indepvar2 = 'N',
  depvar = 'State Government Expenditure per Capita',
  depvar2 = 'ExpPC',
  coef = -0.96,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.18
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 1,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 1,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.213,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.018
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 2,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.229,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.037
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 3,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.455,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.038
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 4,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.411,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.049
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 1,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.226,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.053
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 2,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.213,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.317
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 3,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.185,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.305
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 4,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.235,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.336
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 5,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.374,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.064
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 6,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.811,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.181
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 7,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.795,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.176
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 8,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.849,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.238
))

dat <- rbind(dat,
  data.frame(
  id = 974,
  published = 'No',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'Latin America',
  title = 'Institutional arrangements and fiscal performance: the latin american experience',
  author = 'Stein, Talvi, and Grisanti',
  year = 1998,
  authoryear = 'Stein et al. (1998)',
  journal = 'NBER Working papers',
  web = 'https://www.nber.org/papers/w6358.pdf',
  table = 3,
  column = 1,
  indepvar = 'District magnitude',
  indepvar2 = 'logN',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.0109,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.0143
))

dat <- rbind(dat,
  data.frame(
  id = 974,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'Latin America',
  title = 'Institutional arrangements and fiscal performance: the latin american experience',
  author = 'Stein, Talvi, and Grisanti',
  year = 1998,
  authoryear = 'Stein et al. (1998)',
  journal = 'NBER Working papers',
  web = 'https://www.nber.org/papers/w6358.pdf',
  table = 3,
  column = 4,
  indepvar = 'District magnitude',
  indepvar2 = 'logN',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.0135,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.0121
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 4,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 1,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.009,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.002
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 2,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.011,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.003
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 1,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.005,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.003
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 1,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.04,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 2,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.03,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 3,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.01,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.002
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 4,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.02,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.004
))

dat <- rbind(dat,
  data.frame(
  id = 886,
  published = 'No',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Brazil',
  title = 'Electoral systems, legislative fragmentation and public spending: a comparative analysis of brazilian states',
  author = 'Lledo',
  year = 2003,
  authoryear = 'Lledo (2003)',
  journal = NA,
  web = 'http://lasa.international.pitt.edu/Lasa2003/LledoVictor.pdf',
  table = 6,
  column = 1,
  indepvar = 'Log (State Legislature Seats)',
  indepvar2 = 'logN',
  depvar = 'Primary Spending as a share of GSP',
  depvar2 = 'PCTGDP',
  coef = -4.69,
  scoef = 'N',
  scoefsig = NA,
  SE = -4.69/(-1.75)
))

dat <- rbind(dat,
  data.frame(
  id = 862,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
  author = 'Schaltegger and Feld',
  year = 2009,
  authoryear = 'Schaltegger and Feld (2009)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
  table = 6,
  column = 4,
  indepvar = 'Seats in Parliament',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.001,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 862,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
  author = 'Schaltegger and Feld',
  year = 2009,
  authoryear = 'Schaltegger and Feld (2009)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
  table = 6,
  column = 3,
  indepvar = 'Seats in Parliament',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.001,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 1,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 3,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.302,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.302/7.885
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 1,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.276,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.276/7.185
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 2,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.295,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.302/7.545
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 1,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 6,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Expenditure Share',
  depvar2 = 'PCTGDP',
  coef = 2.066,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.066/7.014
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 4,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Expenditure Share',
  depvar2 = 'PCTGDP',
  coef = 2.012,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.012/6.701
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 5,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Expenditure Share',
  depvar2 = 'PCTGDP',
  coef = 2.468,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.468/8.251
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 1,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.014,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 2,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = -0.011,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.009
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 5,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.007,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.007
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 6,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.005,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.009
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 7,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.005,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.009
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 10,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.012,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.007
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 1,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 1,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.016,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 2,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.021,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.011
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 3,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.014,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.009
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 4,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.003,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.006
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 6,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.03,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.026
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 7,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.030,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.026
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 8,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.039,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.021
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 9,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.0127,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.014
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 10,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.016,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 578,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districting and Government Overspending',
  author = 'Baqir',
  year = 2002,
  authoryear = 'Baqir (2002)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
  table = 4,
  column = 4,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'ln(Government expenditure per capita)',
  depvar2 = 'logExpPC',
  coef = 0.1127,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.0373
))

dat <- rbind(dat,
  data.frame(
  id = 578,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districting and Government Overspending',
  author = 'Baqir',
  year = 2002,
  authoryear = 'Baqir (2002)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
  table = 4,
  column = 1,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'ln(Government expenditure per capita)',
  depvar2 = 'logExpPC',
  coef = 0.276,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.0384
))

dat <- rbind(dat,
  data.frame(
  id = 578,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districting and Government Overspending',
  author = 'Baqir',
  year = 2002,
  authoryear = 'Baqir (2002)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
  table = 4,
  column = 2,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'ln(Government expenditure per capita)',
  depvar2 = 'logExpPC',
  coef = 0.3021,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.0383
))

dat <- rbind(dat,
  data.frame(
  id = 578,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districting and Government Overspending',
  author = 'Baqir',
  year = 2002,
  authoryear = 'Baqir (2002)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
  table = 4,
  column = 3,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'ln(Government expenditure per capita)',
  depvar2 = 'logExpPC',
  coef = 0.3203,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.0384
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 4,
  indepvar = 'Seats in lower chamber',
  indepvar2 = 'N',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.82,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.19
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 1,
  indepvar = 'Seats in lower chamber',
  indepvar2 = 'N',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -1.7,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.31
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 2,
  indepvar = 'Seats in lower chamber',
  indepvar2 = 'N',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -2.37,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.37
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 3,
  indepvar = 'Seats in lower chamber',
  indepvar2 = 'N',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -2.03,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.37
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 4,
  indepvar = 'Seats in upper chamber',
  indepvar2 = 'K',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.97,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.74
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 1,
  indepvar = 'Seats in upper chamber',
  indepvar2 = 'K',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 5.9,
  scoef = 'P',
  scoefsig = 'P',
  SE = 1.64
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 2,
  indepvar = 'Seats in upper chamber',
  indepvar2 = 'K',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 5.75,
  scoef = 'P',
  scoefsig = 'P',
  SE = 1.73
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 3,
  indepvar = 'Seats in upper chamber',
  indepvar2 = 'K',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 6.96,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.22
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 1,
  indepvar = 'Lower chamber size',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = -2.04,
  scoef = 'N',
  scoefsig = NA,
  SE = 1.33
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 1,
  indepvar = 'Lower chamber size',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = -1.40,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.64
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 1,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 26.09,
  scoef = 'P',
  scoefsig = 'P',
  SE = 7.45
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 1,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 8.3,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.35
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 2,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 5.14,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.53
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 3,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 4.78,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.9
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 2,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 20.38,
  scoef = 'P',
  scoefsig = 'P',
  SE = 6.47
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 3,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 4.87,
  scoef = 'P',
  scoefsig = 'P',
  SE = 1.83
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 4,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 26.75,
  scoef = 'P',
  scoefsig = 'P',
  SE = 13.21
))

dat <- rbind(dat,
  data.frame(
  id = 439,
  published = 'Yes',
  usemeta = 1,
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Legislative term limits and state spending',
  author = 'Erler',
  year = 2007,
  authoryear = 'Erler (2007)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/27698198',
  table = 2,
  column = 1,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 3.93,
  scoef = 'P',
  scoefsig = NA,
  SE = 1.18
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 3,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.136,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.136/2.92
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 1,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.2319,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.2319/4.56
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 2,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.1443,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.1443/2.91
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 4,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.1594,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.1443/3.05
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 5,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.2259,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.2259/4.04
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 1, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 5,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.159,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.041
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 6,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.147,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.041
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 7,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.09,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.038
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 8,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.081,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.039
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 9,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.088,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.038
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 1,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.21,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.023
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 2,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = .157,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.037
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 3,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.199,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.04
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 4,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.169,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.041
))

dat <- rbind(dat,
  data.frame(
  id = 231,
  published = 'Yes',
  usemeta = 1, 
  method = 'IV',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Germany',
  title = 'Coalition governments, cabinet size, and the common pool problem: evidence from the german states',
  author = 'Baskaran',
  year = 2013,
  authoryear = 'Baskaran (2013)',
  journal = 'European Journal of Political Economy',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0176268013000773?token=FECF22AE9B176134ACEB47AC0F11ACEFB1EA36D2D73BE992E1471732604540D3DCBD2D4A9CFDE2E44BE0B65C947FA4E3',
  table = 3,
  column = 4,
  indepvar = 'Parliament seats',
  indepvar2 = 'N',
  depvar = 'Real Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.974,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.974/1.743
))

dat <- rbind(dat,
  data.frame(
  id = 230,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislatures, Leaders and Leviathans',
  author = 'Maldonado',
  year = 2013,
  authoryear = 'Maldonado (2013)',
  journal = 'Social Science Quarterly',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
  table = 2,
  column = 2,
  indepvar = 'Size lower chamber',
  indepvar2 = 'N',
  depvar = 'Government Share of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.0609,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.0117
))

dat <- rbind(dat,
  data.frame(
  id = 230,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislatures, Leaders and Leviathans',
  author = 'Maldonado',
  year = 2012,
  authoryear = 'Maldonado (2012)',
  journal = 'Social Science Quarterly',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
  table = 2,
  column = 2,
  indepvar = 'Size upper chamber',
  indepvar2 = 'K',
  depvar = 'Government Share of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.04,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.0132
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 1,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = -0.003,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 3,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = -0.006,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 2,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending (%) GDP',
  depvar2 = 'PCTGDP',
  coef = -0.004,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.02
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 4,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending (%) GDP',
  depvar2 = 'PCTGDP',
  coef = -0.008,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.02
))

dat <- rbind(dat,
  data.frame(
  id = 208,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
  author = 'Kessler',
  year = 2014,
  authoryear = 'Kessler (2014)',
  journal = 'Journal of Political Economy',
  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
  table = 2,
  column = 4,
  indepvar = 'Council size',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.174,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.085
))

dat <- rbind(dat,
  data.frame(
  id = 208,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
  author = 'Kessler',
  year = 2014,
  authoryear = 'Kessler (2014)',
  journal = 'Journal of Political Economy',
  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
  table = 2,
  column = 1,
  indepvar = 'Council size',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.223,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.052
))

dat <- rbind(dat,
  data.frame(
  id = 208,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
  author = 'Kessler',
  year = 2014,
  authoryear = 'Kessler (2014)',
  journal = 'Journal of Political Economy',
  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
  table = 2,
  column = 2,
  indepvar = 'Council size',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.215,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.061
))

dat <- rbind(dat,
  data.frame(
  id = 208,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
  author = 'Kessler',
  year = 2014,
  authoryear = 'Kessler (2014)',
  journal = 'Journal of Political Economy',
  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
  table = 2,
  column = 3,
  indepvar = 'Council size',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.158,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.054
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 1,
  indepvar = 'Upper chamber (senate) seats',
  indepvar2 = 'K',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 8.21,
  scoef = 'P',
  scoefsig = 'P',
  SE = 4.051
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 2,
  indepvar = 'Upper chamber (senate) seats',
  indepvar2 = 'K',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 8.423,
  scoef = 'P',
  scoefsig = NA,
  SE = 18.17
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 3,
  indepvar = 'Upper chamber (senate) seats',
  indepvar2 = 'K',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 9.594,
  scoef = 'P',
  scoefsig = 'P',
  SE = 3.804
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 1,
  indepvar = 'Lower chamber (senate) seats',
  indepvar2 = 'N',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = -0.351,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.745
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 2,
  indepvar = 'Lower chamber (senate) seats',
  indepvar2 = 'N',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 5.975,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.646
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 3,
  indepvar = 'Lower chamber (senate) seats',
  indepvar2 = 'N',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 7.658,
  scoef = 'P',
  scoefsig = 'P',
  SE = 3.922
))

dat <- rbind(dat,
  data.frame(
  id = 8,
  published = 'Yes',
  usemeta = 1, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'Local',
  location = 'Indonesia',
  title = 'Legislature size, local government expenditure and taxation, and public service access in indonesia',
  author = 'Lewis',
  year = 2019,
  authoryear = 'Lewis (2019)',
  journal = 'Studies in Comparative International Development',
  web = 'https://link.springer.com/content/pdf/10.1007/s12116-019-09278-1.pdf',
  table = 4,
  column = NA,
  indepvar = 'Legislature size',
  indepvar2 = 'N',
  depvar = 'Log per capita total expenditure',
  depvar2 = 'logExpPC',
  coef = -0.174,
  scoef = 'N',
  scoefsig = 'N',
  SE = (-0.174+0.245)/1.96
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 1,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.851,
  scoef = 'N',
  scoefsig = NA,
  SE = 1.395
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 2,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -1.689,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.697
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 3,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 7.632,
  scoef = 'N',
  scoefsig = NA,
  SE = 2.309
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 1,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 19.74,
  scoef = 'P',
  scoefsig = 'P',
  SE = 8.406
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 2,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 10.06,
  scoef = 'P',
  scoefsig = 'P',
  SE = 3.965
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 3,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 9.062,
  scoef = 'P',
  scoefsig = NA,
  SE = 20.38
))

dat <- rbind(dat,
  data.frame(
  id = 82,
  published = 'Yes',
  usemeta = 1, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'Local',
  location = 'Germany',
  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
  author = 'Höhmann',
  year = 2017,
  authoryear = 'Höhmann (2017)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
  table = 2,
  column = 1,
  indepvar = 'Total number of seats in the legislature',
  indepvar2 = 'N',
  depvar = 'Log expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.03,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 82,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'Local',
  location = 'Germany',
  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
  author = 'Höhmann',
  year = 2017,
  authoryear = 'Höhmann (2017)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
  table = 2,
  column = 2,
  indepvar = 'Total number of seats in the legislature',
  indepvar2 = 'N',
  depvar = 'Log expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.03,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 82,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'Local',
  location = 'Germany',
  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
  author = 'Höhmann',
  year = 2017,
  authoryear = 'Höhmann (2017)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
  table = 2,
  column = 3,
  indepvar = 'Total number of seats in the legislature',
  indepvar2 = 'N',
  depvar = 'Log expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.04,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.02
))

dat <- rbind(dat,
  data.frame(
  id = 102,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Australia',
  title = 'The price of democracy? political representation structure and per capita expenditure in victorian local government',
  author = 'Drew and Dollery',
  year = 2017,
  authoryear = 'Drew and Dollery (2017)',
  journal = 'Urban Affairs Review',
  web = '10.1007/s11127-016-0369-9',
  table = 2,
  column = 1,
  indepvar = 'No. of representatives',
  indepvar2 = 'N',
  depvar = 'Ln Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.077,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.028
))

dat <- rbind(dat,
  data.frame(
  id = 102,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Australia',
  title = 'The price of democracy? political representation structure and per capita expenditure in victorian local government',
  author = 'Drew and Dollery',
  year = 2017,
  authoryear = 'Drew and Dollery (2017)',
  journal = 'Urban Affairs Review',
  web = '10.1007/s11127-016-0369-9',
  table = 2,
  column = 2,
  indepvar = 'No. of representatives',
  indepvar2 = 'N',
  depvar = 'Ln Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.031,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.022
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 1,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 0.0164,
  scoef = 'P',
  scoefsig = NA,
  SE = 1.313
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 1,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 38.44,
  scoef = 'P',
  scoefsig = 'P',
  SE = 19.23
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 2,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 37.85,
  scoef = 'P',
  scoefsig = 'P',
  SE = 17.77
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 3,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 25.61,
  scoef = 'P',
  scoefsig = 'P',
  SE = 13.48
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 4,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 5.996,
  scoef = 'P',
  scoefsig = 'P',
  SE = 13.06
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 5,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 25.56,
  scoef = 'P',
  scoefsig = 'P',
  SE = 13.49
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 6,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 4.693,
  scoef = 'P',
  scoefsig = NA,
  SE = 12.35
))

dat <- dat[order(dat$id),]
dat <- dat[!is.na(dat$coef),]
row.names(dat) <- NULL
levels(dat$elecsys2) <- c('Majoritarian', 'Non-Majoritarian')
dat$scoef <- factor(as.character(dat$scoef), labels = c('N', 'P'))
dat$scoefsig <- factor(as.character(dat$scoefsig), labels = c('N', 'P'))
levels(dat$scoef) <- c('Negative', 'Positive')
levels(dat$scoefsig) <- c('Negative', 'Positive')
dat$method <- factor(as.character(dat$method), 
                     levels = c("OLS", "PANEL", "IV", "RDD"))
dat$location2 <- as.character(dat$location)
dat$location2[dat$location2!='World'] = 'Country'
dat$location2 <- factor(as.character(dat$location2), 
                     levels = c("Country", "World"))
dat$agglevel <- factor(as.character(dat$agglevel), 
                     levels = c("Local", "States", "Countries"))
fulldat <- dat
dat <- dat %>%
  filter(usemeta == 1)
```
\newpage
## Descriptive statistics

### Study Year

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
dat %>%
  ggplot(aes(x = as.factor(year))) + 
    geom_bar(color = "black") + 
  labs(x = "",
       y = "") + 
  theme_bw()
```

\newpage
### Published?

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
dat %>%
  ggplot(aes(x = as.factor(published))) + 
    geom_bar(color = "black") + 
  labs(x = "Published study?",
       y = "") + 
  theme_bw()

```

\newpage
### Dependent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
dat %>%
  mutate(depvar2 = factor(depvar2, 
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") + 
  labs(x = "Dependent Variables",
       y = "") + 
  coord_flip() + 
  theme_bw()

```

\newpage
### Independent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
dat %>%
  mutate(indepvar2 = factor(indepvar2, labels = c('K (upper house legislators)',
                                                  'N (lower house legislators)',
                                                  'Log N'))) %>%
  ggplot(aes(x = indepvar2)) + 
    geom_bar(color = "black") + 
  labs(x = "Independent Variables",
       y = "") +
  coord_flip() +
  theme_bw() 
```

\newpage
### Histogram Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Coefficients"}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") + 
  labs(x = "Coefficients") + 
  theme_bw()

```

\newpage
### Histogram Standard Errors

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Standard Errors"}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") + 
  labs(x = "Standard Errors") + 
  theme_bw()

```

\newpage
### Sign Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign?"}
dat %>%
  ggplot(aes(x=as.factor(scoef))) + 
  geom_bar(color = "black") + 
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

A general test of the theory would be to study whether the coefficients are positive or negative. Note that the law of 1/n would pose that we should have a positive influence of legislature size on expenditure. To test this theory, we run a Binomial One-Proportion Z-test. For the number of legislators in the lower house (N), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2 == 'N')
# str(aux$scoef) -- Obs: this line originally was in the main text. Fix? - LMM
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```


Therefore, the most elementary test we could run, a sign direction test, tells us that the law of 1/n does not hold for our sample. For the number of legislators in the upper house (K), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2 == 'K')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

Here, the law of 1/n holds. However, the effect goes in a direction different from the predicted in the law of k/n paper.

\newpage
### Electoral system

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral system"}
dat %>%
  ggplot(aes(x=as.factor(elecsys2))) + 
    geom_bar(color = "black") + 
  labs(x = "Electoral system",
       y = "") + 
  theme_bw()
```

\newpage
### Electoral system x Sign Coefficient

```{r, echo=FALSE}
table(dat$scoef, dat$elecsys2)
chisq.test(table(dat$scoef, dat$elecsys2), simulate.p.value = T)
```

\newpage
### Independent Variable x Sign Coefficient

```{r, echo=FALSE}
table(dat$scoef, dat$indepvar2)
chisq.test(table(dat$scoef, dat$indepvar2), simulate.p.value = T)
```

\newpage
### Dependent variables x Independent variables

```{r, echo=FALSE}
table(dat$scoef, dat$depvar2)
chisq.test(table(dat$scoef, dat$depvar2), simulate.p.value = T)
```

\newpage
## Meta-analysis

We combined the three independent variables (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.

### ExpPC x N

```{r, echo=FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()


f1 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f1
ggsave("./plots/f1.png", width = 20, height = 10, units = "cm")

```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
#### Electoral system subgroup analysis

The law of 1/n was created for majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary electoral system.

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)

mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()


f1b <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f1b
```

Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved. The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08. Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.

\newpage
### PCTGDP x N

This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.

```{r}
# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f2 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f2
ggsave("./plots/f2.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### logExpPC x N

This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.

```{r}
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod <- metagen(
  coef, SE, data=aux, 
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction = TRUE,
  sm="SMD"
  )

mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()


f3 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f3
ggsave("./plots/f3.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### ExpPC x logN

There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.

### PCTGDP x logN

This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.

```{r}
# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

mod <- metagen(
  coef, SE, data=aux, 
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction=TRUE,
  sm="SMD"
  )

mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f4 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f4
ggsave("./plots/f4.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### logExpPC x logN

In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).

```{r}
# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()


f5 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f5
ggsave("./plots/f5.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### ExpPC x K

Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).

```{r}
# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()


f6 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f6
ggsave("./plots/f6.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### PCTGDP x K

This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).

```{r}
# Pooling effects analysis -- PCTGDP x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()


f7 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f7
ggsave("./plots/f7.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`


\newpage
### logExpPC x K

No studies related the log of per capita expenditure with the size of upper house (K).


```{r, echo=FALSE, fig.width=12.5, fig.height=5}

#grid.arrange(f8, f9, f11, 
#             f10,f12, f13,
#             f14,
#             ncol = 2,
#             nrow = 4)
#library(ggplot2)

blank = ggplot() + 
  geom_blank() +
  theme_minimal()
blank
ggsave("./plots/zz_blank.png", width = 20, height = 10, units = "cm")

plots = list.files(path = "./plots/", pattern = "*.png") %>%
  map(~{
    image_rotate(image_read(path = paste0("./plots/", .x)), 270)
  })

p_1 = image_append(c(plots[[3]], plots[[2]], plots[[1]]), stack = T)
p_2 = image_append(c(plots[[6]], plots[[5]], plots[[4]]), stack = T)
p_3 = image_append(c(plots[[15]],plots[[7]],plots[[15]]), stack = T)
p_full = image_append(c(p_1, p_2, p_3))

p_full

#p_full

#ggpubr::ggarrange(plots[[1]],plots[[2]],
#                  plots[[3]],plots[[4]],
#                  plots[[5]],plots[[6]],
#                  plots[[7]],
#                  nrow = 4, ncol = 2
#                  )

#ggpubr::ggarrange(f1,f2, 
#          labels = c("A", "B"),
#          ncol = 1, nrow = 2)

#grid.draw(rbind(f1,f2, size = "first")) 


#plot_grid(f1,f2 + rremove("x.text"), 
#          labels = c("A", "B"),
#           align = "v", nrow = 2, rel_heights = c(1/4, 1/4))
```



\newpage
## Meta-Analysis (all coefficients)

### ExpPC x N

```{r, echo=FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f8 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f8
ggsave("./plots/f8.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
#### Electoral system subgroup analysis

The law of 1/n was created for majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary electoral system.

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f8b <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f8b
```

Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved. The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08. Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.

\newpage
### PCTGDP x N

This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.

```{r}
# Pooling effects analysis -- PCTGDP x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B"))

f9 <- mod2 %>%
  ggplot(aes(y = reorder(studlab,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f9
ggsave("./plots/f9.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### logExpPC x N

This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.

```{r}
# Pooling effects analysis -- logExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()


f10 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f10
ggsave("./plots/f10.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### ExpPC x logN

There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.

### PCTGDP x logN

This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.

```{r}
# Pooling effects analysis -- PCTGDP x logN
aux <- fulldat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()


f11 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f11
ggsave("./plots/f11.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### logExpPC x logN

In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).

```{r}
# Pooling effects analysis -- logExpPC x logN
aux <- fulldat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f12 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f12
ggsave("./plots/f12.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### ExpPC x K

Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).

```{r}
# Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()


f13 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f13
ggsave("./plots/f13.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### PCTGDP x K

This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).

```{r}
# Pooling effects analysis -- PCTGDP x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()


f14 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 

f14
ggsave("./plots/f14.png", width = 20, height = 10, units = "cm")
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

### logExpPC x K

No studies related the log of per capita expenditure with the size of upper house (K).


```{r, echo=FALSE, fig.width=10, fig.height=1}

#grid.arrange(f8, f9, f11, 
#             f10,f12, f13,
#             f14,
#             ncol = 2,
#             nrow = 4)
#library(ggplot2)

blank = ggplot() + 
  geom_blank() +
  theme_minimal()
blank
ggsave("./plots/zz_blank.png", width = 20, height = 10, units = "cm")

plots = list.files(path = "./plots/", pattern = "*.png") %>%
  map(~{
    image_rotate(image_read(path = paste0("./plots/", .x)), 270)
  })

p_1 = image_append(c(plots[[10]], plots[[9]], plots[[8]]), stack = T)
p_2 = image_append(c(plots[[13]], plots[[12]], plots[[11]]), stack = T)
p_3 = image_append(c(plots[[15]],plots[[14]],plots[[15]]), stack = T)
p_full = image_append(c(p_1, p_2, p_3))

p_full

#p_full

#ggpubr::ggarrange(plots[[1]],plots[[2]],
#                  plots[[3]],plots[[4]],
#                  plots[[5]],plots[[6]],
#                  plots[[7]],
#                  nrow = 4, ncol = 2
#                  )

#ggpubr::ggarrange(f1,f2, 
#          labels = c("A", "B"),
#          ncol = 1, nrow = 2)

#grid.draw(rbind(f1,f2, size = "first")) 


#plot_grid(f1,f2 + rremove("x.text"), 
#          labels = c("A", "B"),
#           align = "v", nrow = 2, rel_heights = c(1/4, 1/4))
```


\newpage
## Meta-regressions

### Meta-regressions for Expenditure as a Percentage of the GDP

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)
```

```{r}
summary(mod)
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, echo=FALSE}
permutest(mod, progbar = F)
```

We have the following results for the meta-regressions of Expenditure Per Capita:

1. Compared with `K`, models with `N` and `logN` find significantly negative coefficients.
2. Year has null effect.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.

Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)
```

```{r}
summary(mod)
```

```{r}
permutest(mod, progbar = F)
```

For all the coefficients, we have the following results:

1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.

### Meta-regressions for Expenditure Per Capita

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear)
```

```{r}
summary(mod)
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, echo=FALSE}
permutest(mod, progbar = F)
```

We have the following results for the meta-regressions of Expenditure Per Capita:

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has null effect.
3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the per capita expenditure found in our models.
4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
5. When passing from `Local` to `State` level, decreases the detected effects.

Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)
```

```{r}
summary(mod)
```

```{r}
permutest(mod, progbar = F)
```

With all coefficients, the results of the effect sizes on the Expenditure Per Capita Regressions are the following:

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has now a positive effect on coefficient sizes.
3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the effects on per capita expenditure found in our models.
4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
5. All other coeffients were not significant.

### Meta-regressions for the Log of Expenditure Per Capita

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)
```

```{r}
summary(mod)
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, echo=FALSE}
permutest(mod, progbar = F)
```

We have the following results for the meta-regressions of Log of Expenditure Per Capita:

1. Unpublished papers report a significantly higher coefficient.
2. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
3. All other coefficients remained insignificant.

Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)
```

```{r}
summary(mod)
```

```{r}
permutest(mod, progbar = F)
```

With all coefficients, the results of the effect sizes on the Log of Expenditure Per Capita Regressions are the following:

1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
2. All other coefficients remained insignificant.

## Theory of Meta Analysis

There are two main estimators for conducting meta analysis: fixed effects and random effects models. The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect. The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.

In this paper, we use the random effects model. The empirical papers testing the law of 1/n are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
2. **Electoral systems**: Majoritarian, PR, Mixed.
3. **Modeling strategies**: Panel data, Standard OLS, IV, RDD.

These sources of heterogeneity have two implications. First, it makes our estimates very disperse. The heterogeneity tests are all but one significant. When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates. Second, the amount of heterogeneity makes fixed effects estimates unrealistic and bised. Thus, we opt for random effects model.

Let each study having an effect of $T_i$. In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ come from, $\theta_i$, and a within-study error $\varepsilon_i$:

\[
T_i \ = \ \theta_i + \varepsilon_i
\]

And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:

\[
T_i \ = \ \mu + \xi_i + \varepsilon_i
\]

And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in (Doing Meta-Analysis with R)[https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html]. To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it as more precise when we have continuous measures, such as we have on our data (link)[https://www.ncbi.nlm.nih.gov/pubmed/26332144].

## Robustness: Full model meta-regressions combined

In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling by:

1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
2. The type of the independent variable in the stydy (N, K, log of N);
3. The electoral system (Majoritarian, Proportional Representation, and Mixed).

The results follow below, and show null effect for all variables, including the intercept.

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha")
```

```{r}
summary(mod)
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, echo=FALSE}
permutest(mod, progbar = F)
```

In the main text, we selected the coefficients based on the regressions that had most observations and that presented a full model (with fixed effects or intermediate bandwidth in RDD). Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha")
```

```{r}
summary(mod)
```

```{r}
permutest(mod, progbar = F)
```

